Well, that happened.

The immediate hot take on the midterm election yesterday is that it was
a Republican sweep here in Ashtabula County. Every Republican got
re-elected. Sarah Fowler Arthur will be returning to the statehouse.
Mike DeWine will serve his second term as Governor of Ohio. Two levy
questions failed in Ashtabula County but otherwise the fifty percent of
the electorate that turned out decided it wanted to have Republicans in
power.

I won't get a partisan breakdown of turnout until the election is
adjudicated and canvassed. That can take up to twenty days after the
election happens. The Thanksgiving holiday will have happened before
those details will be known. What irks me greatly is that Republicans in
the area decided to turn out \emph{this time} and couldn't be bothered
last year to turn out to support the only Republican on the ballot in
the only contested municipal race. Yeah, I am referring to my loss last
year where I wound up getting more votes from \emph{Democrats} due to
how few Republicans bothered to show up to vote.

Of course, I'm pretty much not a Republican by today's standards. I have
pretty publicly come out against MAGA. I've certainly condemned Sarah
quite a bit in print throughout 2022 in fairly consistent terms. I am a
Kinzinger-Cheney Republican which is to say I am part of a disappearing
breed.

Currently control of Congress is hanging in the balance. Maybe we'll
have a clearer picture in the morning but frankly I doubt it.

There are 670 absentee ballots still outstanding. There are 478
provisional ballots requiring adjudication after the ten day cure period
expires. I don't think any of the races were too close this time to
where outcomes will flip. Outcomes have flipped due to provisional
ballots in the past in this county, mind you.

The only good news is that the supermajority is broken in the
statehouse. It continues in the Ohio Senate but the GOP wound up two
seats short of a supermajority in the Ohio House. In terms of the
trifecta that means legislation can't easily be rammed through. They
have to either notionally talk to two Democrats to secure their votes or
everything will wind up having appropriations attached. My guess is that
token appropriations will be attached to every piece of legislation for
the next two years.

The pro-infection/anti-vaxx candidates got elected. Ultimately this is
bad for me. I am as up to date on my shots but now I'm rolling the dice
continuing to live in Ohio. That gives me something to sleep on, I
suppose.
