I will complain a little about the bullying on various Mastodon sites
relative to the use or the lack of use of ``Content Warning'' functions.
The thread started with a post by Aleen Simms at
\url{https://wandering.shop/@aleen/109545360209489228} shows people
beating up on her for no good reason. The bullying, denigration, and
worse is frankly uncalled for. Aleen has a very good point when it comes
to artists promoting their work.

I don't miss ``starving artists'' shows at the I-X Center near Cleveland
Hopkins Airport. They were frequent features being advertised while I
was growing up in Cleveland. Social media outlets have reduced the need
for them \emph{somewhat} these days but with Twitter dying and Facebook
going downhill we're shifting back to that.

All this debate over the use of content warnings on Mastodon is getting
ridiculous. We didn't need them in the days of StatusNet. We didn't have
them on pump.io. GNU Social didn't have them. \texttt{Diaspora*} didn't
have them. Despite the claims that ``original gangsta'' people in the
fediverse have used content warnings since the beginning they're
actually an innovation that did \textbf{not} exist until 2016. Yes, that
does mean that for the first eight years of the fediverse \emph{there
were no content warnings at all}. I was there in the beginning of the
fediverse over fourteen years ago. Many of these ``OG tooter'' people
are simply posers who ignore that which came before.

There is a reason I try to write as much as I can in my blog. In short,
it is \textbf{my} blog. I don't really intend to use content warnings. I
want to follow the science
\href{https://theconversation.com/proceed-with-caution-the-trouble-with-trigger-warnings-192598}{as
mentioned by a couple Australian professors} that these warnings
probably aren't all that useful.

I wander into the weirdest parts of the Internet, I guess.
