I gave my class their first test of the session on Wednesday night. It
appeared to go well. I'm still not happy with the time compression I had
to shift to but I will have to live with it. I accidentally revealed
this domain in class but if any of them see this blog they'll probably
see that I am human.

The meeting of the Broadband Task Force went well in Jefferson. We have
things moving forward! Ohio Transparent Telecom is actually moving ahead
with installing nodes on MARCS towers and elsewhere so that we can have
``fixed wireless'' on offer to residents. OTT is a participant in the
Affordable Connectivity Program so we won't have too many issues
reaching residents cost-wise. This is possibly going to get some good
uptake. The ``middle mile'' project is also progressing quite nicely
too.

Early voting continues in the general election. About eighty percent of
absentee ballots have been returned. Once of my biggest concerns is that
people think that somehow the absentee ballots get better with age. They
truly don't! If any of them try to follow the idiocy from the Lindell
people and try to return their absentee ballots at their precinct
polling places they will be finding nasty surprises that the precincts
\emph{are not allowed to accept those ballots} and such voters will be
required to vote provisional ballots until things get straightened out.
Democratic Party usage of early/absentee ballots is outstripping
Republican Party usage in the county. That doesn't translate to
significant turnout by Republicans on Election Day, though.

My vision problems were starting to flare back up last night and that
scared the crap out of me. No,
\href{http://web.archive.org/web/20221103142320/https://my.clevelandclinic.org/health/diseases/24335-central-serous-retinopathy}{central
serous chorioretinopathy} is not fun. There are certain things that can
be done to manage it but it will never truly go away. Truly this is a
thorn in the flesh.

I'm still learning how to best utilize my Apple Watch. The health data
it is producing has already been quite useful. Other functions and
features aren't truly critical as the health data is key.

I need to look at getting
\href{http://web.archive.org/web/20220913101141/http://www.nncpgo.org/}{NNCP}
running with a portal node. With war not abating any time soon and the
Internet fracturing it seems like time is coming to revert to older
styles of communication. I'm not saying it is totally time to be running
something on \href{https://www.fidonet.org/index.html}{the dog network}
once again but perhaps that may change soon.

\href{https://youtu.be/QY9oWfkKt6A}{Be seeing you\ldots{}}
