In no particular order:

\begin{itemize}
\tightlist
\item
  I suppose I need to look at
  \href{https://github.com/buckket/twtxt}{twtxt} a bit.
\item
  I had not planned on opening an account on a Mastodon node any time
  soon yet \href{https://mas.to/@smkellat}{it seemed to have happened
  anyhow}.
\item
  The network connection bounced at church during service Sunday. That
  caused the livestream to be disrupted. The
  \href{https://youtu.be/ygrygzUnsL8}{recording had to be posted after
  service} to replace the incomplete stream recording that
  \href{https://www.youtube.com/channel/UCs1dDMVsjKcgeOynUXZkZww}{YouTube
  had} on the channel. Surprisingly
  \href{https://www.twitch.tv/GenevaChurchOfChrist}{Twitch} was able to
  handle the bounce a bit better.
\item
  Even though today is Election Day I am \emph{not} working a polling
  place today. I had to stand down for this election on account of a
  conflict caused by the employer.
\item
  I'm not looking forward to the outcome of the poll. I'll likely be
  watching \href{https://liveresults.ohiosos.gov/}{the state-level
  tracker for state rep seats} to see if Kathy Zappitello wins.
\item
  Making progress on weight loss plans is still a goal. Whether it is
  \href{https://www.nasmbwpcalculator.com/}{one calculator} or
  \href{https://www.niddk.nih.gov/bwp}{another} I have to move forward.
\item
  I am still learning more about the INTJ mess. It explains quite a few
  things.\\
\item
  I will be enjoying \emph{The Mads Are Back} in lieu of fretting over
  election results with the network news live coverage Tuesday night. I
  already voted early. I'm expecting results to be weird as it is.
\item
  I'm getting to the point of not wanting to plan all that far ahead. I
  can't really say that I am taking life day-by-day but planning more
  than a week ahead is getting increasingly counterproductive. A time
  for reassessment is coming.
\end{itemize}
