Well, everybody's least favorite cult leader went ahead and announced
his \emph{formal} resumption of campaigning for the presidency of the
United States of America. He practically never stopped after he lost in
2020. He just made it official Tuesday that he is back in the running
for a primary that won't even be happening until \textbf{2024}. It was
very painful to watch the speech he gave from Mar-A-Lago as it had very
little connection to reality and sound more like what you'd hear from a
patient in a psych ward.

And yet, he could very well win the GOP primary if nobody can
sufficiently stand up to him. That disturbs me greatly. Family commented
during the speech that the former president sounded like he was giving a
psychological permission slip for yet another coup attempt. The unstated
message in the framing of the event was how much it called back to the
events arranged by the German film director Leni Riefenstahl for that
infamous dictator who sparked a major worldwide conflict. Looking at a
clip from one of her films
\href{https://archive.org/details/hitler-delivers-speech-at-nuremberg-night-rally-1934}{on
the Internet Archive} compared to some of the recent rallies really
gives me the creeps considering how close the visual design is between
the two scenes.

Family know that I want to relocate to Australia or Canada. Such things
are easy to say but relatively complicated to implement. As life here
gets increasingly weirder I'm going to eventually need to come to some
conclusions as to how I want to handle things. The upcoming outcomes are
not looking too good for far too many people.
