Once more with feeling\ldots{}

\begin{itemize}
\tightlist
\item
  Twitter is becoming more of a nightmare.

  \begin{itemize}
  \tightlist
  \item
    The explore tab is now quite full of QAnon-related and
    antivaxx-related content.
  \item
    My mentions tab now recommends QAnon-related and antivaxx-related
    content to me.
  \item
    Debirdify isn't picking up any more Mastodon handles being added to
    Twitter profiles so what I have is what I have, I think.
  \item
    There is a push to bring even more MAGA craziness back to Twitter.
    That has implications for societal cohesion.
  \item
    Limited reports indicate that the Twitter CEO is refusing to pay the
    rent on commercial properties utilized by the company. The evictions
    could get very interesting.
  \end{itemize}
\item
  Very little else is happening in my life at the moment.

  \begin{itemize}
  \tightlist
  \item
    The COVID-19 pandemic helped ensure many of the social circles that
    existed prior for me would cease to exist.
  \item
    Being in the wintry season brings about complications for me too.
    Access to parks is limited due to snow. Even if the snow melts there
    is still a possible subsidence danger until the groundwater table
    handles all the melt.
  \item
    I really don't need too many material things that I don't otherwise
    have. I won't be going ``battle shopping'' on Friday.
  \item
    My personal library collection is over three hundred volumes now and
    I may need to actually do some weeding.
  \end{itemize}
\item
  Politics is getting weird locally.

  \begin{itemize}
  \tightlist
  \item
    I've essentially napalmed most bridges this year in terms of making
    any runs as a candidate.
  \item
    In a pretty public fashion I have disassociated myself from what is
    now the mainstream of thought in the Republican Party. I am not
    pro-MAGA by any stretch of imagination.
  \item
    Two at-large seats on Ashtabula City Council are up for election in
    2023 \emph{are} up for election.

    \begin{itemize}
    \tightlist
    \item
      I stand very little chance of success running as an independent.
    \item
      The two spots are basically more aggravation than they're worth.
    \end{itemize}
  \item
    If a presidential appointment with senate confirmation or a
    gubernatorial appointment with senate confirmation was on offer I
    would quite possibly consider it. The likelihood of any such thing
    being on offer is less than me winning the lottery. Anybody
    interested in nominating me can look at the Plum Book as to federal
    positions, I suppose. The Governor of Ohio's home page has a section
    listing positions too plus a form to nominate people to him.
  \end{itemize}
\item
  There are no clear plans for 2023.

  \begin{itemize}
  \tightlist
  \item
    Nothing is really certain right now.
  \item
    Unless I get offered a work tasking I'll be back to planning no more
    than two weeks ahead.
  \item
    No grand plans are even in mind right now.
  \end{itemize}
\item
  Life is just very weird these days.
\end{itemize}
