In no particular order:

\begin{itemize}
\tightlist
\item
  There is some sort of holiday later this week, I suppose.

  \begin{itemize}
  \tightlist
  \item
    I am still working this week
  \item
    I am still working Wednesday night
  \end{itemize}
\item
  Increasingly I end up convinced that Gerry Anderson's vision of the
  future is what our world is converging towards in far too many ways.

  \begin{itemize}
  \tightlist
  \item
    The Antonov An-225 leaves me wondering when exactly
    \emph{Thunderbirds} first aired in the Soviet Union, for example.
  \item
    We're less than 40 years away from the time when the story of
    \emph{Thunderbirds} and \emph{Stingray} was said to take place.
  \end{itemize}
\item
  I'm not happy about the ``Content Warning'' drama in Mastodon land.

  \begin{itemize}
  \tightlist
  \item
    While I was writing this in Visual Studio Code it automatically
    offered to open a GitHub Issue for me, strangely enough.
  \item
    In the end, my personal settings on \href{https://mas.to/}{mas.to}
    expand all such taggings by default.

    \begin{itemize}
    \tightlist
    \item
      I can survive looking at such things usually.
    \item
      It annoys me heavily having to click through all of them to get at
      content. That drove me back to Twitter when the ``Content
      Warning'' banners got way too excessive.
    \end{itemize}
  \item
    Either this will pass eventually or there will be a schism. My money
    is on a schism.
  \end{itemize}
\item
  I am trying out share buttons on my Jekyll pages. Hopefully it works
  okay.
\item
  It is still cold and messy outside. This climate is not great for me.
\end{itemize}
