In a somewhat peculiar order:

\begin{itemize}
\tightlist
\item
  Getting 17 inches of snow on Thursday was not amusing.

  \begin{itemize}
  \tightlist
  \item
    Getting the snow plowed was a pain
  \item
    We had snow emergencies declared by the sheriff for the first time
    in \emph{decades} on Thursday
  \item
    The snow happened Thursday and my car only got unburied on
    \emph{Friday}
  \end{itemize}
\item
  \href{https://en.wikipedia.org/w/index.php?title=Torchy_the_Battery_Boy&oldid=1114309923}{``Torchy
  The Battery Boy''} is premium nightmare fuel, it seems
\item
  Twitter is imploding

  \begin{itemize}
  \tightlist
  \item
    Some reports indicate the company is down to ten percent of the
    headcount it had on the day before Elon Musk took control
  \item
    The engineers required to keep systems running are now gone
  \item
    Despite people claiming online rather earnestly that the banks that
    backed the deal will earnestly attempt to keep Twitter running there
    is the slight problem of staffing. Software engineers are not
    interchangable widgets. Twitter is a complicated, complex product
    with some homegrown components. People with the relevant domain
    knowledge walked away. Anybody who is brought in will have to be
    brought up to speed on something that will be ultimately foreign to
    them and might be impossible for them to master.

    \begin{itemize}
    \tightlist
    \item
      What could go wrong?
    \item
      Since there are some ``invented here'' pieces of the Twitter tech
      stack the loss of so many engineers leads to the problem of
      finding replacements. Could anybody step in to replace those who
      left? If they can't find anybody the site's days are going to
      start running out.
    \end{itemize}
  \item
    API failures are increasing as the day goes on
  \item
    I can't successfully post there now
  \end{itemize}
\item
  I am still looking at things like
  \href{https://medium.com/illumination/livestreaming-to-twitch-using-a-command-prompt-92f5f862af16\#:~:text=Livestreaming\%20to\%20Twitch\%20Using\%20a\%20Command\%20Prompt\%201,command\%20...\%205\%20Step\%205\%3A\%20Go\%20Live\%21\%20}{this
  post to Medium} in terms of setting up semi-unattended streaming from
  the Raspberry Pi 4.

  \begin{itemize}
  \tightlist
  \item
    The big push for this is to create a online television station on a
    shoestring for the local area.
  \item
    People flailing about without access to reliable information sources
    during Thursday's Level 3 Snow Emergency is a big reason for this.

    \begin{itemize}
    \tightlist
    \item
      Facebook is not a reliable source of information.
    \item
      Local radio stations all broadcast feeds from distant networks and
      have no local air talent. They're no help.
    \item
      Our ``local'' television stations are based in Cleveland and cover
      a 17 county area equal in size to the Commonwealth of
      Massachusetts. We're an afterthought to them more often than not.
    \end{itemize}
  \item
    Considering how many people locally think Facebook is the answer for
    all their information-seeking needs we may have a few problems
    having this accepted

    \begin{itemize}
    \tightlist
    \item
      This is a high COVID-denialism area and high COVID transmission
      area
    \item
      Culturally this area is extremely reactionary rather than
      accepting of new things
    \item
      Facebook is treated like AOL was treated 25-30 years ago
    \end{itemize}
  \end{itemize}
\item
  Church continues to be interesting

  \begin{itemize}
  \tightlist
  \item
    Livestreaming for \href{https://genevachurchofchrist.org}{Geneva
    Church of Christ} continues
  \item
    I will be preaching for the regular morning service on December 11th
  \end{itemize}
\item
  Other projects

  \begin{itemize}
  \tightlist
  \item
    Not everything can be openly stated yet
  \item
    Other irons are in the fire, though
  \end{itemize}
\end{itemize}
