In no particular order:

\begin{itemize}
\tightlist
\item
  I've sectioned off from the
  \href{https://code.launchpad.net/~skellat/+git/auto-newspaper}{main
  repo on Launchpad} a test run of the newspaper code and
  \href{https://bitbucket.org/kellat/kellat.bitbucket.io/src/main/}{slapped
  it up on Bitbucket}.

  \begin{itemize}
  \tightlist
  \item
    A single leaf of legal-size paper is probably the best that can be
    managed right now.
  \item
    I don't have any reporting staff.
  \item
    I don't really have bulk printing capability at the moment either.
  \item
    This is the easiest thing to get off the ground at the moment.
  \item
    I \emph{do} have \href{https://issuu.com/coyoteworks}{a basic
    account on issuu} but uploading LaTeX output there requires a wee
    bit more work yet to be appropriately usable.
  \item
    This might be something that could be launched in 2023

    \begin{itemize}
    \tightlist
    \item
      Delivery logistics would be a problem
    \item
      Pricing would be an issue
    \item
      This would need a staff, too
    \end{itemize}
  \item
    My second job ever was as a writer for a newspaper so I have
    confidence that I could make \emph{something} happen

    \begin{itemize}
    \tightlist
    \item
      The first job? Custodian.
    \item
      I have no regrets about the first job. I got it while I was still
      in high school. The money earned from that let me participate in
      the foreign exchange in high school and visit Paris as well as
      southern France in 1998. I haven't been to Europe this century but
      I have been to Europe.
    \end{itemize}
  \end{itemize}
\item
  My stress levels have been a bit elevated. How can I tell? Impacts
  related to the diagnosed rare eye disease are how I can tell.
\item
  The biggest thing through the COVID-19 pandemic is the idiotic
  response by many Americans that if someone doesn't kill you you'll be
  able to get through it and be fine on the other side of your struggle.
  Those ignorant fools don't understand how there are so many ways human
  beings can be crippled by illnesses and diseases. That just bothers me
  greatly in so many ways. Those bumptious fools have likely never lived
  with chronic conditions of any sort so that whole realm of experience
  is alien to them yet I know it rather well.
\item
  The poor people in Buffalo are getting pounded with even more snow.
  They're getting close to the five feet mark again. I don't envy
  them.\\
\item
  I have to get out to Robot Zero Comics in Geneva eventually. They have
  a couple things in that I ordered. IDW has published some comic books
  with further adventures of the various \emph{Star Trek} shows that
  explicitly tell stories that fall between the airing seasons.
  Considering how much unwatchable crap is on the television lately and
  that there is no new \emph{Star Trek} airing at the moment I shouldn't
  dawdle on picking up my order.

  \begin{itemize}
  \tightlist
  \item
    It feels weird getting into comic books as an adult.
  \item
    I have a wonderful collection of regular books at home so comic
    books are just another type of item in the home library.
  \end{itemize}
\item
  I need to listen to the free story from Big Finish Productions that I
  downloaded that Ian Potter wrote. First up I have to finish listening
  to the Captain Scarlet story I am listening to.
\item
  I'm striking out on the current dating app. There are just way too
  many explicitly antivaxx people who are vocal in their profiles to hit
  ``PASS'' on right now.
\end{itemize}
