For this early on a Friday we now turn to a miscellany of brief items.
In no particular order:

\begin{itemize}
\tightlist
\item
  A very good podcast is
  \href{https://gerry-anderson-randomiser.captivate.fm}{The Gerry
  Anderson Randomiser}. It has been a joy to listen to in the car while
  commuting between home and the work sites.
\item
  I have \href{https://pypi.org/project/feed2toot/}{\texttt{feed2toot}}
  configured on a free tier VM on Oracle's cloud. It will auto-post new
  blog entries to the Mastodon instance found at \url{https://mas.to}.
\item
  Another very good podcast is
  \href{https://www.theincomparable.com/gameshow/trivia/}{Random
  Pursuit}. I think I am current and have listened to the whole back
  catalog of that show now.
\item
  Discussed with my Licensed Professional Clinical Counselor who has
  training in treating trauma issues the whole debate over the infamous
  ``content warning'' matters on Mastodon. She finds the huge amount of
  ``content warning'' tagging to be odd.\\
\item
  Winter is coming and I am not looking forward to it this year. Wintry
  times give me a push to move to places like the Pacific or the
  Caribbean. The weather of northeast Ohio is just getting to me.
\item
  As I am not Roman Catholic or Lutheran I am removed a wee bit from the
  social structures of the community. Community leaders in my local area
  are generally part of those denominational traditions. It is very
  possible to still be a Christian and not be Roman Catholic or Lutheran
  but it radically changes your social circles in this town.
\item
  I am still shocked we doubled down on bad governance in the recent
  election here in Ohio. We're going to have a state legislature chasing
  its tail starting in January rather than attempting to meet the actual
  practical priorities of the average citizen.
\item
  My career in politics is toast.
\item
  Writing can be good for weight loss. How so? Sometimes you just need
  to let everything out. Microblogging on Twitter and Mastodon is too
  short of a format to make such work well. Longer blogging styles let
  you gather your thoughts, express yourself clearly, and express
  emotions potentially. Getting your cortisol levels under control by
  writing about how things are going is a useful adjunct to daily
  exercise.
\item
  I have to unbury the treadmill. Winter is coming.
\item
  Understanding living with a smartwatch is still a challenge for me.
\item
  I need to get back to writing fiction. There is an aborted start to a
  fourth story. It essentially train-crashed into a narrative dead-end.
  I'm likely going to have to start from the top with something new.
\item
  There may be an attempt at \href{https://www.kcrw.com/radio-race}{the
  KCRW Radio Race} this weekend. Last year I entered but couldn't come
  up with anything within the time limit. Maybe I will have luck this
  year?
\end{itemize}
