A miscellany in no particular order:

\begin{itemize}
\tightlist
\item
  I didn't leave the house today due to the arctic conditions. When the
  wind chill is almost thirty degrees below zero it is perhaps a bit too
  dangerous. Fairport Harbor over in Lake County saw hurricane force
  winds from this nastiness.
\item
  Development of the over-the-top network is stalled. I have ordered a
  new Raspberry Pi 4B+ from PiHut in the UK. That'll likely be used as a
  streaming head-end. The problem is where the head-end would stream to
  in actual operations.

  \begin{itemize}
  \tightlist
  \item
    I really want to do a teletext carousel to push out on Twitch like
    TCI/Adelphia had on the old 1990s cable system on Channel 30. That
    would help with the lack of prepared content at the moment. YouTube
    has an example \href{https://youtu.be/bhw25jFm5So}{out of
    Minneapolis} that presents the idea roughly.
  \item
    I haven't finished putting my query together to fetch an appropriate
    weather conditions map from the National Digital Forecast Database.
    That would be helpful to use in pushing a weather report in a
    semi-automated fashion.
  \item
    A goal of such a project is to \textbf{NOT} do something like
    \href{https://vimeo.com/783282497}{this} from
    \href{https://vimeo.com/user126359532}{Conneaut CAT-TV} if we can
    help it.
  \item
    Something arranged like \href{https://geaugatv.org/contact}{Geauga
    G-TV} would probably work but we would ditch running on a cable
    system to be online only. They have
    \href{https://vimeo.com/gtvvideos}{video on-demand} on Vimeo. Their
    work is funded via franchise fees received locally in Geauga County.
  \item
    This still needs work.
  \end{itemize}
\item
  The Christmas Eve service at Geneva Church of Christ should prove
  interesting. It \textbf{WILL} be streamed live on Twitch at
  \url{https://www.twitch.tv/GenevaChurchOfChrist/} starting at 2330 UTC
  on Christmas Eve.
\item
  The set of \emph{Computer Chronicles} episodes that I tagged on the
  experimental podcast feed over on the \href{https://coyote.works}{ELP
  Television} site is at a healthy number. The podcast feed has more
  programs in it than display on the site.
\item
  I still haven't finished wrapping Christmas presents. I suppose I
  should do that.
\item
  I want to move somewhere warmer than Ashtabula. The Caribbean sounds
  nice. Moving back to American Samoa sounds nice too. Brisbane would be
  fun if I could somehow manage it. Until I feel comfortable enough
  getting all issues on the chart to being ``well-managed'' these can
  only be dreams.

  \begin{itemize}
  \tightlist
  \item
    I've already lived in American Samoa and it is a lush and verdant
    place.
  \item
    I've visited part of the Caribbean.
  \item
    I haven't yet quite managed to visit Australia notwithstanding
    trying to find ways to do so.
  \end{itemize}
\item
  Dating apps at this time of the year are not fun.
\end{itemize}
