Right now we are heading into dangerous times. There was a political
convention meeting over the weekend that had speakers, who happened to
be elected officials talking about having portions of their populace
``eradicated''. A former elected chief executive openly talked about
military intervention in the country's cities to impose ``law and
order'' as well as bringing the imposition of mandatory death penalties
for a variety of sex crimes. That same former chief executive also
called himself the people's ``instrument of retribution'' who could
avenge the wrongs members of his party have faced since he was ousted
from office.

In any other country on the planet where this sort of stuff is going
down this is normally a prelude to a refugee crisis. This is normally a
prelude to something very, very bad happening in a country. Countries
fall when major political parties start trying to normalize extremism
like this.

That may be why I have such a problem that I'm referring to things said
by Marjorie Taylor Greene and Donald John Trump at the Conservative
Political Action Conference this weekend in National Harbor, Maryland.
There is nothing conservative about wanting to ``eradicate'' the
nation's transgender population. There is nothing conservative about
wanting to ignore the Posse Comitatus Act and put troops in the streets
to impose order.

There is no ``letter to the editor'' submission to \emph{The Gazette}
this week. It is increasingly unsafe to do things like that. In a
pro-MAGA community like this you can't say things like what I've just
written above without blowback.

Remember, going full metal MAGA is the path to madness.
