Late on Monday night I lost broadband access at home.

On Tuesday morning I learned that a forced firmware upgrade was pushed
by Windstream to its combo router/modem units. Fortunately the optical
network transceiver was not impacted by this forced firmware upgrade.
The bad part to this is that the forced upgrade \emph{bricked the unit}.

Windstream's automated customer service agent helpfully indicated that
they would ship out a new combo router/modem to me and it would arrive
within 3-5 business days after Monday. There's no rollback in the
interim. It isn't like I can hook up a Morse Code key to get by using
the optical network transceiver by itself.

I visited Harbor-Topky Memorial Library to pick up a hotspot from them.
The hotspot on loan uses Verizon's network. Unfortunately Verizon is not
a network you can easily access within my house. We're also only on a 4G
LTE network out here in Ashtabula County even though the hotspot is
billed as being ``5G'' capable. You do what you can with what is
available.

All this means is that I'm going to be very, very absent online for the
time being. There is no proper estimated time for restoration. At this
point I am waiting to see when equipment arrives and if it survives
being hooked up in place of the dead gear.

Yes, there is a hotspot on my AT\&T prepaid wireless phone. That is
metered and has a relatively low cap. I'm taking advantage of it to post
this blog post. Things will reset on the 10th as to my phone. Between
now and then I have to stretch things out.

This is going to be complicated. I haven't been able to reach a human at
Windstream. I don't expect to be able to do so either.

Ah, the joys of life in Ashtabula\ldots{}
