I mark many things in \href{https://netnewswire.com/}{NetNewsWire} as
being interesting and worthy of further review. The list of feeds being
watched is
\href{https://code.launchpad.net/~skellat/+git/FeedReadingFeeds}{maintained
as an OPML file in a git repo}. Some of those items marked in the RSS
reader include but are not limited to:

\begin{quote}
\emph{\href{https://www.bbc.co.uk/news/world-us-canada-64883668?at_medium=RSS&at_campaign=KARANGA}{Republicans
slam Fox News' Tucker Carlson over Capitol riot clips}}
\end{quote}

Yeah, I was referring to this yesterday. Apparently I was not the only
person horrified by what Tucker Carlson did.

\begin{quote}
\emph{\href{https://scrippsnews.com/stories/why-has-the-tech-industry-had-massive-layoffs/}{Why
has the tech industry had massive layoffs?}}
\end{quote}

Scripps News gives us their spicy take on the situation.

\begin{quote}
\emph{\href{https://scrippsnews.com/stories/what-to-know-about-new-breakthrough-weight-loss-drugs/}{Everything
you need to know about new breakthrough weight loss drugs}}
\end{quote}

This borders on being an advertorial, it seems.

\begin{quote}
\emph{\href{https://pxlnv.com/linklog/bill-c-18-after/}{Bill C--18,
After Facebook and Google}}
\end{quote}

Nick Heer gives us a glimpse of the impending death spiral for Canada's
news industry.

\begin{quote}
\emph{\href{https://electionlawblog.org/?p=135002}{``Why Arizona's
attorney general is suing Cochise County for giving its recorder control
over elections''}}
\end{quote}

Rick Hasen points out in Election Law Blog a bad situation in Arizona
that is not stopping any time soon. Cochise County had to be sued to be
forced to certify the results from the 2022 election as it was.
Delegating the board's responsibility to a single individual who happens
to be an elections conspiracist seems to be regrouping after getting
smacked down in court just a few months ago.

\begin{quote}
\emph{\href{https://electionlawblog.org/?p=135000}{``Trump, Vowing
`Retribution,' Foretells a Second Term of Spite; In a speech before his
supporters, the former president charged forward in an uncharted
direction, talking openly about leveraging the power of the presidency
for political reprisals.''}}
\end{quote}

Yeah, Election Law Blog points out the doom.

\begin{quote}
\emph{\href{https://taxprof.typepad.com/taxprof_blog/2023/03/chatgpts-tax-advice-was-wrong-100-of-the-time.html}{ChatGPT's
Tax Advice Was Wrong 100\% Of The Time}}
\end{quote}

TaxProf Blog brings us the \textbf{totally and utterly expected} news
that ChatGPT gives bad tax advice. I am so ready for ``ChatGPT told me
to do it'' to be added to the
\textbf{\href{https://www.irs.gov/privacy-disclosure/the-truth-about-frivolous-tax-arguments-introduction}{frivolous
tax arguments}} listing that
\href{https://www.irs.gov/privacy-disclosure/the-truth-about-frivolous-tax-arguments-section-iii}{results
in civil penalties and consequences that should make people think
twice}. There's already a nasty little
\href{https://www.irs.gov/newsroom/irs-warns-taxpayers-of-new-filing-season-scams-involving-form-w-2-wages-those-filing-fake-returns-face-potential-penalties-investigation}{scheme
floating around on social media} that is going to get
``TikTok/Facebook/Whatever told me to do it'' added, I think.

\begin{quote}
\emph{\href{https://www.taxpayeradvocate.irs.gov/news/nta-blog-standard-mileage-deduction-rates/}{NTA
Blog: Standard Mileage Deduction Rates Should Be Consistent for All
Taxpayers}}
\end{quote}

This is a prime example of the consequences of Congress not thinking
about the consequences of the legislation it writes.

\begin{quote}
\emph{\href{https://netblocks.org/reports/mobile-internet-disrupted-in-mauritania-following-prison-break-3An41by2}{Mobile
internet disrupted in Mauritania following prison break}}
\end{quote}

This is such a horrible way of handling this sort of thing.

\begin{quote}
\emph{\href{https://daringfireball.net/linked/2023/03/06/cpan-knowles-nazi}{CPAC
Speaker Michael Knowles Calls for Transgender People to Be `Eradicated
From Public Life Entirely'}}
\end{quote}

Bad things are coming. We have people in the Republican Party trying
very hard to get revisionist with history to make the events of the
Capitol riot disappear. Ideological conformity is being pushed through a
rise in book bannings across the country. We have people at CPAC calling
for the ``eradication'' of classes of human beings.

This isn't going to burn out. These people
\href{https://scrippsnews.com/stories/donald-trump-tells-cpac-crowd-i-am-your-retribution/}{want
a clash}. How they're dealt with is going to be a huge problem.

\begin{quote}
\emph{\href{https://hackaday.com/2023/03/06/whats-going-to-happen-to-legacy-broadcast-bands-when-the-lights-go-out/}{What's
Going To Happen To Legacy Broadcast Bands When The Lights Go Out?}}
\end{quote}

I disagree with this on so many levels.

\begin{quote}
\emph{\href{https://hackaday.com/2023/03/06/the-future-of-risc-v-and-the-visionfive-2-single-board-computer/}{The
Future of RISC-V and the VisionFive 2 Single Board Computer}}
\end{quote}

I'll start to think RISC-V is going somewhere when I have it running
Xubuntu in a usable form.

\begin{quote}
\emph{\href{https://www.abortretry.fail/p/a-short-history-of-berkeley-risc}{A
Short History of Berkeley RISC}}
\end{quote}

A good read.

\begin{quote}
\emph{\href{https://www.avclub.com/the-daytime-tv-apocalypse-continues-as-rachael-ray-anno-1850187651}{The
daytime TV apocalypse continues as Rachael Ray announces she's packing
it in}}
\end{quote}

Our economy is in worse shape than it seems at initial glance.
