From time to time it is a good idea to look at the starred items in my
feed reader. It isn't quite a literature review when this is done. It
isn't quite an annotated bibliography. It is just a look at what caught
my eye across so many RSS feeds.

In no particular order:

\begin{itemize}
\tightlist
\item
  In a post entitled
  \href{https://steve.cooleysekula.net/blog/2023/01/09/some-tips-on-setting-up-a-mastodon-instance-using-docker-and-apache/}{``Some
  Tips on Setting Up a Mastodon Instance Using Docker and Apache''},
  Dr.~Steve Sekula writes down some notes on setting up Mastodon.
  Dr.~Sekula is a brave self-hoster with lots of history in the
  fediverse dating back to \texttt{StatusNet} and \texttt{pump.io}.\\
\item
  Apparently I am not the only one unamused by changes to the TV app as
  MacRumors has a post entitled
  \href{https://www.macrumors.com/2023/01/09/tvos-16-2-watch-now-design-complaints/}{``Apple
  TV Users Complain About tvOS 16.2 `Watch Now' Redesign''}. I'm not
  holding my breath for a revert on the change.\\
\item
  AV Club teases with the headline
  \href{https://www.avclub.com/star-trek-picard-team-why-show-ending-with-season-3-1849966879}{``Star
  Trek: Picard team discusses why the show is ending with season 3''}
  and doesn't really deliver much of anything in its post.
\item
  Apparently the
  \href{https://www.ctan.org/ctan-ann/id/mailman.3032.1673290313.3715.ctan-ann@ctan.org}{scripture
  package on CTAN was updated} which will prove useful if I have to put
  devotional materials again in the future.\\
\item
  NBC is investing in \href{https://www.nbcnews.com/now}{NBC News Now}
  apparently as \emph{Variety} reports that
  \href{https://variety.com/2023/tv/news/gadi-schwartz-nbc-news-streaming-anchor-1235482553/}{``Gadi
  Schwartz To Anchor Streaming 8PM Hour for `NBC News Now'\,''}
\item
  TechRadar tells us that
  \href{https://www.techradar.com/news/microsoft-now-wants-to-add-chatgpt-to-word-email}{``Microsoft
  now wants to add ChatGPT to Word, email''} which makes LibreOffice,
  NextCloud, and Collabora Online look so much better.
\item
  \href{https://mt-shortwave.blogspot.com/2023/01/radio-habana-cubas-arnaldo-arnie-coro.html}{Arnie
  Coro passed away}
\item
  JSTOR Daily brings us
  \href{https://daily.jstor.org/on-your-mark-get-set-print/}{``On Your
  Mark, Get Set\ldots{} Print!''} which is just incomprehensible to
  think about in 2023.
\item
  \emph{Cleveland Scene} brings us word that
  \href{https://www.clevescene.com/news/ohio-gov-mike-dewine-signs-citizenship-status-voter-id-bill-41182933}{Governor
  Mike DeWine signed the election restrictions bill} that will make life
  interesting this year.
\item
  Are there shortwave radio broadcast airchecks from the invasion in
  Brasilia of the legislature there?
  \href{https://swling.com/blog/2023/01/carlos-shortwave-art-and-recording-of-china-radio-international-invasion-of-brazilian-congress-january-8-2023/}{Yes}.
\item
  We see in \emph{Variety} that the disturbing matter of shows being
  terminated even after orders are made continues with
  \href{https://variety.com/2023/tv/news/pantheon-canceled-season-two-amc-plus-1235481759/}{AMC
  axing a show even though it finished production}. This is also
  reported by
  \href{https://www.avclub.com/amc-cancels-61st-street-tosses-already-filmed-second-s-1849960939}{AV
  Club}.
\item
  The Disruptive Library Technology Jester brings us discussion in
  \href{https://dltj.org/article/generating-podcast-transcripts/}{``Automatically
  Generating Podcast Transcripts''}
\item
  Lizbeth Myles brings up the matter of
  \href{https://lmmyles.com/2023/01/06/the-ages-of-the-actors-whove-played-doctor-who/}{``The
  Ages of the Actors Who've Played Doctor Who''}.
\item
  Apparently
  \href{https://www.avclub.com/edward-norton-related-to-pocahontas-1849953198}{Edward
  Norton is a distant relative to former Heidi Heitkamp among many, many
  other people}. BBC News
  \href{https://www.bbc.co.uk/news/world-us-canada-64158055}{talked
  about this too}.
\item
  Alan Pope talks about
  \href{https://popey.com/blog/2023/01/year-of-the-broken-desktop/}{``Year
  of The Broken Desktop''} in his blog.
\item
  Apparently the launch from Cornwall of a satellite on Monday was a
  failure
  \href{https://www.france24.com/en/europe/20230110-virgin-orbit-s-groundbreaking-satellite-launch-ends-in-failure}{per
  France24}. The Russia-Ukraine conflict is damaging our access to space
  since the plant for making rocket motors was damaged as well as much
  of the Antonov company's facilities and fleet. The destruction of the
  Antonov An-225 Mriya in the Battle of Anotonov Airport possibly
  heavily impacts the US space program since nobody else on the planet
  has a heavy lifter with that much capacity and NASA previously used it
  to ferry spacecraft bits to Plum Brook Station for testing outside
  Sandusky.
\end{itemize}

There are many other things stashed among the starred stories but these
were highlights worth sharing.
