A story posted recently brought some minor and not so minor concerns to
mind. CBS News
\href{https://web.archive.org/web/20230528070548/https://www.cbsnews.com/news/senators-issued-satellite-phones-new-security-measures/}{reported}
that federal senators were being issued sat phones. The story went on to
say that fifty out of the one hundred senators accepted them. All that
was said about the phones was that they're being deployed to ensure a
redundant and secure means of communication during a disruptive event.

That sounds ominous. Nowhere in the article is there any indication as
to what sort of event is being planned against. We're simply supposed to
take it on faith that this is just a normal, regular, every day
occurence in our federal government.

The comments on \emph{Hacker News} as seen at
\url{https://news.ycombinator.com/item?id=36096342} do not shed much
light on the situation. The most recent
\href{https://web.archive.org/web/20230529132640/https://www.dhs.gov/sites/default/files/ntas/alerts/23_0524_S1_NTAS-Bulletin-508.pdf}{National
Terrorism Advisory System bulletin} makes it seem like something
\emph{may} be cooking out there. Our infrastructure in the United States
is still far too vulnerable than we like to admit.

I suppose we'll see what erupts. I'm not running out to buy an
\href{https://web.archive.org/web/20230503042400/https://bivystick.com/}{ACR
Bivy Stick} right just yet. That's quite a bit of cost for very
uncertain and quite possibly uncertain payoff right now.
