Currently the Republican caucus in the United States House of
Representatives is blocking a vote to raise the ``debt ceiling'' as they
\href{https://www.msn.com/en-us/news/politics/factbox-u-s-house-republicans-many-proposals-for-spending-cuts-in-debt-ceiling-debate/ar-AA170JkU}{want
to cut federal spending}. They want to do this so that they can balance
the budget in their view and reduce the amount of the debt. The catch is
that they \emph{do not} want to raise taxes and \emph{do not} want to
cut Social Security/Medicare/Medicaid, Defense spending, or Veterans
spending.

Fortunately the nice folks at Treasury
\href{https://fiscaldata.treasury.gov/americas-finance-guide/federal-spending/\#spending-categories}{have
a report showing a breakdown of federal outlays}. If you section off
those four categories, you're protecting roughly sixty one percent of
the budget. The ``Income Security'' category is broader than just
Medicaid but for these purposes we'll leave it and its generally related
programs like SNAP in there.

With more than half the budget protected from cuts you end up wondering
what is left. Another two percent relates to ``general government'' and
that includes must have items like operating the treasury and the mint
in addition to keeping our ability to conduct foreign relations. If you
cut those things frankly we would not have much of a functioning federal
government left. The
\href{https://thehill.com/finance/3849874-here-are-the-spending-cuts-republicans-have-pitched-in-debt-limit-talks/}{plans
are not quite fully thought out} as we see in reports.

The clock keeps ticking as X Day draws nearer. With all the
pre-conditions they have before making any cuts frankly Republicans
would be looking at closing agencies and cabinet departments wholesale
to reap and financial savings. The big four areas they're trying to
ring-fence are the costliest items in the entire budget. In contrast to
spending on the big four, spending on Homeland Security only takes up
one percent of the budget. Relatively speaking we spend a negligible
pittance on NASA and less than half of NASA's budget topline is what was
appropriated for the National Science Foundation this past year. As much
as the National Endowment for the Arts has been a target of Republicans
it only got two hundred seven million dollars in the most recently
enacted budget. Abolishing the Arts endowment wouldn't lead to much in
terms of budget savings.

This is all absurd. Where is the voice of reason? We're heading too
easily to sovereign default. Unfortunately there are no voices in DC
calling for this matter to be resolved for the good of the nation so
that we can move forward.

We are blessed with politicians who are more incompetent than usual.
