The Internet is certainly full of crap. I've currently got the blogroll
looking like this:

\begin{itemize}
\tightlist
\item
  \href{https://www.theincomparable.com/gameshow/actioncastle/}{Action
  Castle and other Parsely Games! (from The Incomparable Game Show)}
\item
  \href{https://popey.com/blog/}{Alan Pope's blog}
\item
  \href{https://www.kryogenix.org/days/}{as days go by (Stuart
  Langridge)}
\item
  \href{https://xubuntu.org/}{Blog - Xubuntu}
\item
  \href{https://critrole.com/shows/candela-obscura/}{Candela Obscura}\\
\item
  \href{https://smoliva.blog/}{Computer Chronicles Revisited}
\item
  \href{https://critrole.com/}{Critical Role}\\
\item
  \href{https://thedragonfriends.com/}{Dragon Friends}
\item
  \href{https://www.theincomparable.com/gameshow/feud/}{Feuding Families
  (from Game Show)}
\item
  \href{https://www.librarian.net/}{Librarian.net}
\item
  \href{https://www.tk421.net/librarylink/}{Library Link of the Day}
\item
  \href{https://lmmyles.com/}{Lizbeth Myles}
\item
  \href{https://www.theincomparable.com/gameshow/lowdef/}{Low Definition
  (from Game Show)}
\item
  \href{https://mwl.io/}{Michael Warren Lucas}
\item
  \href{https://open-web-advocacy.org/}{Open Web Advocacy}
\item
  \href{https://princessleia.com/journal}{pleia2's blog}
\item
  \href{https://www.publicnewsservice.org/}{Public News Service}
\item
  \href{https://www.theincomparable.com/robot/}{Robot or Not?}
\item
  \href{https://gerry-anderson-randomiser.captivate.fm}{The Gerry
  Anderson Randomiser}
\item
  \href{https://swling.com/blog}{The SWLing Post}
\item
  \href{https://tidbits.com/}{TidBITS}
\item
  \href{https://www.theincomparable.com/gameshow/uktriv/}{UK Triv (from
  Game Show)}
\item
  \href{https://www.relay.fm/ungeniused}{Ungeniused}\\
\item
  \href{http://www.uctv.tv}{University of California Television}
\end{itemize}

Is it random? Pretty much. Is it full of judgment calls? YES! I could
totally add \href{http://totalkill.party/}{Total Party Kill} to the list
as that has been a thing keeping me going lately. Of course, the stories
from \href{https://www.bigfinish.com/}{Big Finish Productions} have
helped too.

Yes, my interests are a bit weird. The news has just be so bleak lately
that I have been trying to \emph{not} follow it. There is escapism and
there is escapism. I really, really do not want to consider what's
looming at least until the primary election which is coming up on March
19, 2024.
