In no particular order:

\begin{itemize}
\tightlist
\item
  I'm stalling on writing the sermon for Sunday. I must get that
  finished ASAP.

  \begin{itemize}
  \tightlist
  \item
    I need to get some UAP-related pictures.
  \item
    I need to get some \emph{Ancient Aliens} pictures, perhaps.
  \item
    Yeah, the lectionary is pointing to a certain passage in 2 Peter.
    This is probably going to go places.
  \end{itemize}
\item
  The feed dropped out twice during Tuesday's livestream of
  \href{https://www.themadsareback.com/event/dimension-5-livestream-screening/}{\emph{The
  Mads Are Back}}. I gave up the second time relative to trying to
  restore the feed.
\item
  I keep fiddling with my followers list on Mastodon.

  \begin{itemize}
  \tightlist
  \item
    I download the CSV export file, edit it, and upload it back with it
    set to ``overwrite''.
  \item
    The main changes I make beyond removing follows in bulk are to turn
    off ``boosts'' on people and to shift people to showing up in
    notifications. I am my own algorithm now, it seems.
  \end{itemize}
\item
  The situation in East Palestine continues to produce horrors

  \begin{itemize}
  \tightlist
  \item
    Yes, a similar situation could happen here in Ashtabula County.
  \item
    Governor Mike DeWine was getting uncharacteristically upset on
    Tuesday relative to the situation involving the train. This is a
    good thing, I think. Hopefully the feds take notice of the governor
    being upset.
  \item
    The whole situation was a no-win scenario when it came to response,
    it seems. There was no good solution. Almost every solution was a
    \emph{bad} solution.
  \end{itemize}
\item
  The dating game looks weird.

  \begin{itemize}
  \tightlist
  \item
    Axios Columbus mentioned on Valentine's Day that
    \href{https://www.axios.com/newsletters/axios-columbus-98c5a5a0-266a-4193-a96f-10630166e816.html?chunk=1&utm_term=emshare\#story1}{❤️
    In Ohio, love is local}

    \begin{itemize}
    \tightlist
    \item
      Ohio is apparently one of the states where you're most likely to
      marry a local
    \item
      Michigan ranks first in terms of states where that occurs while
      Ohio is fifth
    \item
      We have very few out of state transplants here in Ohio
    \item
      In the aggregate, interstate marriages are on the rise across the
      country which makes Ohio an outlier
    \end{itemize}
  \item
    I'm off any dating apps at the moment. I seemingly cannot devote the
    attention to correctly use such programs.
  \item
    There are many bad prospects in my immediate area.
  \item
    Depending upon the test results that I am waiting on from the
    hospital this may be mooted
  \end{itemize}
\item
  Now should be a good time in life yet isn't really

  \begin{itemize}
  \tightlist
  \item
    They're already discussing the situation in East Palestine on UCTV
    from University of Palestine, it seems
  \item
    My body heat levels keep bouncing around weirdly. Is my thyroud
    taking the weird approachh to functioning?
  \item
    I'm waiting on potentially earth-shattering test results
  \item
    Economic malaise has apparently set in
  \end{itemize}
\item
  I'll be on the hunt for commercial real estate again soon. The weird
  practice locally of selling buildings at two to seven times what the
  county auditor values them at for taxation boggles my mind. These
  aren't very attractice places to begin with\ldots{}
\end{itemize}
