Work continued Monday on getting to operational readiness for the video
podcast. I posted to the Internet Archive
\href{https://archive.org/details/coming-soon-to-elp-tv}{a ``coming
soon'' animatic with audio} and also ensured
\href{https://coyote.works/2023/coming-soon.html}{its presence in the
video podcast feed}. Tools like
\href{https://en.wikipedia.org/wiki/Keynote_(presentation_software)}{Keynote},
\href{https://en.wikipedia.org/wiki/IMovie}{iMovie}, and
\href{https://en.wikipedia.org/wiki/GarageBand}{GarageBand} were used to
put that together. If
\href{https://en.wikipedia.org/wiki/LibreOffice_Impress}{LibreOffice
Impress} had the capability to export to video I would have used it
instead and would probably have used
\href{https://en.wikipedia.org/wiki/OpenShot}{OpenShot} to do the video
editing.

I have started work on a
\href{https://code.launchpad.net/~skellat/+git/show-prep-scripts}{shell
script} to download using \href{https://curl.se/}{cURL} the relevant
bits from the
\href{https://en.wikipedia.org/wiki/National_Weather_Service}{National
Weather Service} to piece together a speaking script semi-automatically.
If I were feeling sufficiently fancy and had sufficient programming
skills \href{https://www.weather.gov/documentation/services-web-api}{I
could use the API to pull data to parse in a more granular fashion}
perhaps. There is
\href{https://web.archive.org/web/20220529113240/https://opendata.stackexchange.com/questions/297/how-does-one-parse-weather-data}{discussion
on StackExchange} as to how such parsing might be done and it is not
nearly as clear as it might appear at first glance.

We're going to launch as soon as possible. The page count of
\href{https://www.starbeacon.com/news/local_news/}{\emph{The Star
Beacon}} is shrinking further. If it gets any smaller it will disappear.
There aren't really slots in
\href{https://web.archive.org/web/20230110060246/https://wkky.com/program-schedule/}{the
schedule of WKKY-FM} showing local news being broadcast. None of the
stations in the \href{http://mediaoneradiogroup.com/}{Media One Radio
Group Ohio cluster} even talk about broadcasting news other than ESPN
Radio on \href{https://en.wikipedia.org/wiki/WFUN_(AM)}{WFUN}.

There is a gap to be filled. Yes, we're starting with just the weather.
After a time we'll add in bits from
\href{https://www.dvidshub.net/search/?q=&filter\%5Btype\%5D=video&filter\%5Bcategory\%5D=Newscasts&view=grid&sort=publishdate}{the
Defense Visual Information Distribution Service} in
\href{https://www.dvidshub.net/search/?q=&filter\%5Btype\%5D=video&view=grid&sort=publishdate}{many
types}. Time will need to be taken to assess the site
\href{https://www.opennewswire.org/}{Open Newswire} to see if material
can be used from it \href{https://opennewswire.org/feed/?language=1}{in
English}.

Progress takes many forms. We're not there yet. We're also only ten days
into the year.
