Am I truly an American? Be careful in how you answer that, dear reader.

Yes, I was born in Cleveland. That means I have citizenship in the
United States of America through our unique practice of birthright
citizenship. That doesn't mean I align very well in the current social
circumstances.

We're seeing very horrible tribalism arise here in the USA. You have a
very religious tribe based in a cult of personality following a
bombastic demagogue. You have tribes that define themselves as
opposition to that tribe of cultists. Other tribes exist, too.

The social fabric is a bit frayed. I don't really align with any of
those tribes all that well. I'm certainly not part of a cult of
personality that worships a coup plotter with plans for dictatorship.
I'm not necessarily a ``progressive'' either as I disagree with some of
the stances of that tribe too. While there used to be a middle ground it
has slowly but surely disappeared as people have taken sides.

The third anniversary of the sacking of the US Capitol is coming up in
just seven days. Have we learned anything from that event? There are
\emph{still} people that deny the event even happened. There are
\emph{still} people desperately seeking out alternate explanations for
that event to be able somehow to say that it was not a coup attempt and
instead some sort of deception. Having watched the attack on live
television that day, I do not doubt that the situation happened.

I keep seeing a notion of ``real American'' propounded that is very,
very far away from what I am. My great-grandfather came to this country
at the start of the 20th century while Teddy Roosevelt was President. It
is an exercise for the reader as to why there are no records of an entry
at Ellis Island but there is record of an entry at \emph{San Francisco}
instead. On my mother's side I had ancestors there to meet the English
when they landed at Jamestown in 1607.

Am I truly an American? In a pre-2015 world the answer would've been yes
as I was proudly helping keep the Machinery of Government as part of the
federal government enterprise. Now, I don't really know. There are scary
times ahead. As people pick sides I'm getting stuck in the middle.
