This is a miscellany of brief items in no particular order. These are
done from time to time on this blog. These are generally things that I
want to express but am not ready to make a complete blog post out of
them.

In no particular order:

\begin{itemize}
\tightlist
\item
  I'll be seeing another medical specialist soon.

  \begin{itemize}
  \tightlist
  \item
    I feel like a lab rat
  \item
    Getting enrolled in a research study kinda makes things feel that
    way
  \item
    When it comes to a matter with a \emph{known} population incidence
    of ``1 in 200,000'' I can't really duck such studies
  \item
    We are learning that there are many modern secular miracles in
    medicine
  \end{itemize}
\item
  My current batch of students will be done on June 5th. My next batch
  starts 15 days later.

  \begin{itemize}
  \tightlist
  \item
    No, I am not a drill instructor.
  \item
    My students learn about computers and gain skills in using them. I'm
    doing something right.
  \item
    I have to do a new ``introducing your faculty member'' video to post
    to Blackboard so that I can swap out the old one.
  \item
    I need to try to author more SCORM content as we head into the
    summer.
  \end{itemize}
\item
  The podcasts tracker is updated at
  \url{https://code.launchpad.net/~skellat/+git/Podcasting}

  \begin{itemize}
  \tightlist
  \item
    Things that are ``private'' or ``members'' feeds do \emph{not}
    appear in the tracker
  \item
    I suppose that means I should reveal myself as a Patreon supporter
    of the \href{https://latenightlinux.com/about/}{Late Night Linux}
    family of programs, I suppose.
  \end{itemize}
\item
  Life has gotten weird
\item
  More strangeness is yet to come, I presume
\end{itemize}
