Let's look at some of the things that caught my eye in
\href{https://netnewswire.com/}{NetNewsWire}.

Scripps News among others has reported
\href{https://scrippsnews.com/stories/us-russia-has-committed-crimes-against-humanity-in-ukraine/}{``US:
Russia has committed crimes against humanity in Ukraine''}.

I thought \emph{The Nevers} was a great show when I watched it over at
the aunt's house. The back half of the show is now finally available
\textbf{but}
\href{https://www.polygon.com/23598491/the-nevers-season-1-free-online-unaired-episodes}{you
have to catch it on Tubi}.

If you are a masochist you apparently
\href{https://www.tomshardware.com/how-to/install-tiny11-for-arm64-on-raspberry-pi-4}{can
install Windows 11 directly to a Raspberry Pi}. That just seems so
suboptimal even though
\href{https://www.techradar.com/news/windows-11-on-raspberry-pi-its-possible-thanks-to-tiny11}{TechRadar
talks about it too}. If you're going to go that far off the beaten path
then
\href{https://www.riscosopen.org/wiki/documentation/show/GUI\%20comparison:\%20RISC\%20OS\%20vs\%20Windows\%20and\%20macOS}{consider
trying RISC OS instead}. Their wiki
\href{https://www.riscos.info/index.php/BeagleBoard-based_Laptop}{even
has discussion of using it to build laptops featuring the BeagleBoard},
oddly enough.

TechRadar is
\href{https://www.techradar.com/news/mac-pro-2023-its-now-or-never-apple-your-customers-are-waiting}{wishcasting
as to seeing an Apple Silicon Mac Pro this year}.

The axe is still swinging at Warner Brothers Discovery as
\href{https://variety.com/2023/tv/news/judge-mathis-the-peoples-court-canceled-warner-bros-1235527589/}{Judge
Mathis and People's Court have been canceled}.

Somebody did a write-up on
\href{https://x61.sh/log/2023/02/20230217T112354-nextcloud_openbsd.html}{running
a Nextcloud server using OpenBSD}.

Karen Kasler reports
\href{https://www.statenews.org/government-politics/2023-02-17/schools-ohio-governments-could-lose-over-a-billion-dollars-from-tax-changes-backed-by-speaker}{that
statehouse legislators are proposing to mess with the state's tax
systems again}. Our state has many issues that \emph{could} be
addressed. Tinkering with the tax systems is not one of the most
pressing problems out there.

People still write about
\href{https://www.complete.org/tools-for-communicating-offline-and-in-difficult-circumstances/}{tools
for communicating in difficult circumstances as well as offline}. Every
day in Ashtabula County could be considered ``difficult circumstances'',
I think.

\{REDACTED\}

Another sad headline:
\href{https://fitnessvolt.com/nashali-alma-fights-off-male-attacker-gym/}{Female
Bodybuilder Nashali Alma Fights Off Male Attacker in Alarming Viral Gym
Video}. People are getting crazy. My main reaction is to wonder why she
didn't clock him with a dumbbell.

Bruce Schneier brings up the very real danger of
\href{https://www.schneier.com/blog/archives/2023/02/defending-against-ai-lobbyists.html}{AI
lobbyists}. Politics is gonna get weird. ChatGPT could accelerate things
like the QAnon cult, it seems.

So, there is a
\href{https://hackaday.com/2023/02/16/bbs-builder-is-a-framework-for-running-your-own-petscii-paradise/}{BBS
Builder available} that people can use. If you run
\href{http://www.syncterm.net}{SyncTerm} you'd be able to access the end
product of using that tool.

Apple is starting an
\href{https://appleinsider.com/articles/23/02/17/apple-tv-needs-more-content-and-they-will-train-directors-to-get-it?utm_medium=rss}{in-house
film school}?

Open Technology Fund, a component of the United States Agency for Global
Media, is
\href{https://www.opentech.fund/news/otf-debrief-introducing-the-shutdown-getdown/}{working
on a summit to counter Internet shutdowns}. This could be a good thing.

COVID raises your risk of diabetes
\href{https://arstechnica.com/?p=1918140}{by 58\%} even with the
supposedly less concerning Omicron spreading around.

The great Les Pounder points out
\href{https://www.tomshardware.com/news/raspberry-pi-retro-news-project}{the
RetroFeed project for Raspberry Pi} that might be something I could
pursue some day. It would make a great piece of set decoration if
nothing else.

Microsoft
\href{https://www.techradar.com/news/microsoft-kills-off-the-enterprise-social-network-no-one-remembered-it-has}{killed
off Yammer finally}.

Microsoft is
\href{https://techcommunity.microsoft.com/t5/microsoft-learn-blog/evolving-microsoft-365-certifications-help-keep-you-in-sync-with/ba-p/3719265}{changing
up its certifications a little bit}.

Our intrepid legislators in Columbus are proposing a new way
\href{https://www.statenews.org/government-politics/2023-02-13/ohio-budget-includes-provision-to-require-social-media-companies-get-parental-permission-for-kids}{to
break the Internet for everybody}.

Somebody is proposing
\href{https://www.tomshardware.com/news/risc-v-laptop-easy-to-build-and-upgrade}{an
ultimate open source laptop} running on RISC-V.

Apparently
\href{https://github.com/chettrick/discobsd?utm_source=discoverbsd}{DiscoBSD}
is a thing.

Netflix has
\href{https://variety.com/2023/tv/news/netflix-removing-arrested-development-original-seasons-1235521721/}{taken
\emph{Arrested Development}} down. Good luck watching it now if you
don't have it in a DVD box set.

LibreOffice is at version 7.5 and
\href{https://www.techradar.com/news/libreoffice-still-thinks-it-can-steal-you-away-from-microsoft-365-or-google-workspace}{competes
against Microsoft 365 apparently now}.

SlashFilm gets fairly direct by saying in their headline:
\href{https://www.slashfilm.com/1187497/in-the-age-of-streaming-tv-preservation-matters-more-than-ever/}{``In
The Age Of Streaming, TV Preservation Matters More Than Ever''}.

All of this was marked in my RSS reader. Enjoy!
