There are some pretty severe complications that arise from the
capitulation to the MAGA faction in the United States House of
Representatives. One of their demands that was memorialized in the
House's rules package was that the infamous debt ceiling would
\textbf{not} be raised without \$130 billion in spending cuts in next
year's budget
\href{https://open.substack.com/pub/heathercoxrichardson/p/january-17-2023?r=2k3po&utm_campaign=post&utm_medium=email}{as
reported by Heather Cox Richardson}. What does that equal? Statista
\href{https://www.statista.com/statistics/200386/budget-of-the-us-government-for-fiscal-year-2012-by-agencies/}{gives
a good breakdown of on-budget budget toplines for the main departments}.
Keeping with the main assumption also made in the MAGA demands that the
military not be cut and that Social Security/Medicare not be cut you
wind up with this being a probable force fit of what that \$130 billion
in cuts would eliminate in whole:

\begin{itemize}
\tightlist
\item
  EPA (\$15 billion)
\item
  Department of Commerce (\$16.7 billion)
\item
  Small Business Administration (\$1.7 billion)
\item
  National Science Foundation (\$9.1 billion)
\item
  NASA (\$24.9 billion)
\item
  Department of the Interior (\$22.8 billion)
\item
  All other on-budget ``independent agencies'' (\$36.1 billion)
\end{itemize}

That leaves \$3.7 billion which probably would be shaved off the \$185
billion budget of the Department of Education. I picked agencies that
have drawn the ire of Republicans over the years and the ones I picked
as likely elimination targets are the usual favorites proposed by the
party. The Republican caucus in the House would probably favor the
imagery of shutting down as many agencies as they could in lieu of only
severely hindering one like the Department of Education.

Would the Senate under the control of the Democrats agree to cuts like
this? No, not really. Could these cuts be done anywhere else? No, not
really. We're potentially heading towards an economic crisis and there
are people in the House deliberately pushing this forward.

Yeah, we'll see how this plays out it seems\ldots{}
