Some days I wish we had the \href{https://youtu.be/cW-5qrwsiOI}{Trumpy}
from MST3K. Saturday was one of those days. Donald Trump was
\href{https://web.archive.org/web/20230319044058/https://www.reuters.com/article/usa-trump-idCAKBN2VK07I}{ranting
online that he thinks he will be arrested on Tuesday the 21st}. He
called for his supported to protest across the country so as to protect
him. The district attorney in Manhattan
\href{https://web.archive.org/web/20230319042422/https://www.politico.com/news/2023/03/18/manhattan-da-bragg-privately-warns-on-intimidation-threats-to-rule-of-law-00087745}{has
already made his reply to Trump's ranting} by indicating that the DA's
office will not be intimidated. The head of the House Republican
Conference, Elise Stefanik,
\href{https://web.archive.org/web/20230319045107/https://twitter.com/elisestefanik/status/1637126158809538563}{made
remarks on Twitter supporting Trump}.

I just have a bad feeling about this. I was alive when the
\href{https://en.wikipedia.org/w/index.php?title=Waco_siege&oldid=1145378099}{Waco
siege} and the
\href{https://en.wikipedia.org/w/index.php?title=Ruby_Ridge&oldid=1145007827}{Ruby
Ridge} incidents took place. This situation could degenerate into being
a siege in Florida pretty quickly. There is reporting that
\href{https://web.archive.org/web/20230319045658/https://www.thedailybeast.com/officials-prep-for-protests-as-maga-sycophants-push-patriot-moat-around-mar-a-lago}{supports
of Donald Trump are planning to mobilize as human shields to protect him
physically from being arrested}. That's the sort of behavior you'd
expect from people involved in that tragedy in Waco.

Things are getting scary right now\ldots{}
