Well, having a day without a working uplink to the Internet has proven
problematical. When you're in a house that is streaming only out in
rural America you end up kissing live streams goodbye. You end up being
reliant on what content you have stored locally.

The hotspot from the library works \emph{but} we have to be careful in
its usage. Service from Verizon in the house is fairly erratic. If we
want to watch anything on television we basically have to terminate use
of Internet on other computing devices or switch them over to other
links if they are even available.

I'm working on bringing up what I can in terms of radio monitoring of
broadcast data streams. The problem there is that I don't have things
configured in convenient ways in convenient places. There are some
frustrating steps to be completed to get that straightened out, it
seems. There are things I can do with SDR dongles here at home but I
have to have things deployable, first.

If I end up creating an airgapped network during this period I will end
up having to leverage \href{http://www.nncpgo.org/}{NNCP}, I think. I am
running out of good ideas.

I will say that I am liking using the Apple Watch as a Bluetooth source
for listening to podcassts. Yes, you can download podcasts to a
relatively current model Apple Watch and play things back to a small
Bluetooth speaker or even headphones directly from the watch. With
episodes saved to the device for playback after loading somewhere I have
ready access to regular high-speed broadband I can still listen to
things without having to fiddle with LTE issues at home or on the go.
That is one bright spot in all of this.
