I'll apparently be attending a symposium at Cleveland Clinic
\href{https://www.clevelandclinicmeded.com/live/courses/pten2023/}{later
this month}. It will be an all-day event on a Monday down in University
Circle. It should be a quite interesting event that I will be attending
\emph{in-person}.

There'll be an open webinar hosted by Penn State
\href{https://networks.h-net.org/node/14775/discussions/12565541/h-teach-online-program-introduction-chatgpt}{dealing
with an introduction to ChatGPT for educators}. I'm signed up for that
event and look forward to it. How we handle ChatGPT in the classroom is
a hot topic right now.

Microsoft has an event on the 16th about
\href{https://news.microsoft.com/reinventing-productivity/}{reinventing
work by using AI}. What could possibly go wrong? It was reported by
\emph{The Verge} that
\href{https://www.theverge.com/2023/2/10/23593980/microsoft-bing-chatgpt-ai-teams-outlook-integration}{it
is supposed to be revealed at this event that ChatGPT is going to be
incorporated into Microsoft's office suite}.

At some point I have ``Lunch and Learn Webinar Series: Recent
Developments in US Foreign Relations Law and Research Strategies'' to
attend online courtesy the
\href{https://www.loc.gov/research-centers/law-library-of-congress/researcher-resources/legal-research-institute/united-states-law-webinars/?loclr=bloglaw}{Law
Library at Library of Congress}. That actually will be fun. I miss being
a librarian. I used to be one of the people conducting bibliographic
instruction not a faculty requester of it.

Is this an idiosyncratic mix? Yes. Bear in mind that the mix of events
listed in the community calendar in \emph{The} (Jefferson, Ohio)
\emph{Gazette} on Wednesday listed only fish fry and pancake breakfast
events. Unfortunately \emph{The Star Beacon} is still shrinking on page
count and I haven't been able to justify picking up a copy at the
current price for so few pages of content to look for events.

I am anchored to northeast Ohio for the time being with the only real
options of other places to live
\href{https://www.ptenresearch.org/for-researchers-and-professionals/projects-and-publications/}{being
Melbourne in Australia and somewhere in the Netherlands}. I have to work
within the limits of my available resources. As much as I might do
better elsewhere, it appears many alternative living locations are
presently foreclosed as options to me.
