Sometimes we need to highlight posts from the fediverse. This will be a
bit of a run of text strings.

Quoting @lauren@mastodon.laurenweinstein.org:
\url{https://mastodon.laurenweinstein.org/@lauren/110489277073189373}
\#retoot

Post by Lauren Weinstein. ``Will public and private reactions to
\#Google's Friday decision to permit 2020 U.S. election denial videos --
of the sort that led to the violent January 6th insurrection -- return
to \#YouTube be reversed by Google after such videos begin appearing
again?'' Posted on Jun 4, 2023 at 22:36

Quoting @frog@frogdrool.net:
\url{https://frogdrool.net/@frog/110489295523523750} \#retoot

Post by frog. ``@lauren If I disable my adblocker, youtube will play ads
like''one simple trick to empty your bowels instantly every night and
melt belly fat''. If they think reversing the decision will make them
more money, they'll do it.'' Posted on Jun 4, 2023 at 22:40

Quoting @mcnulla@techhub.social:
\url{https://techhub.social/@mcnulla/110489328615024918} \#retoot

Post by McNulla. ``@lauren Sucks because now I gotta figure out how to
replace Google: drive, gmail, calendar, voice, etc.'' Posted on Jun 4,
2023 at 22:49

Quoting @xethos@mastodon.xethos.net:
\url{https://mastodon.xethos.net/@xethos/110489535351356035} \#retoot

Post by xethos. ``@mcnulla In order, QNAP NAS + Wireguard, Posteo,
Nextcloud, and Voip.ms Sharing via external links (like one would with
GDrive) from the QNAP is pretty easy, to the point my parents have one
of their own - which provides both of us with an offsite backup. Posteo
support is both real, and helpful - they even knew, immediately, what my
issue was when syncing to my BlackBerry Q10, several years after
BlackBerrys stopped being a thing for most people.'' Posted on Jun 4,
2023 at 23:41

Well, folks can find Nextcloud at \url{https://nextcloud.com} and the
VoIP provider \url{https://voip.ms/} exists too. Posteo is out there at
\url{https://posteo.de/en} and QNAP sells all sorts of products at
\url{https://www.qnap.com/en-us}. For those who need to migrate away
from the Alphabet empire this frankly would be a decent start. Getting
past using Android would still be a bit of an issue, though.

We'll see what happens down the pike, I suppose.
