You would be better off watching a silent film like
\href{https://archive.org/details/moonshiner}{\emph{The Moonshiner}}
than looking at much of the reporting of Tuesday's judicial proceedings
relative to Donald Trump. It was truly a mess. Watching
\href{https://archive.org/details/computersandtechvideos?query=fediverse}{some
videos about the fediverse} probably would be even more beneficial.

In short, he was arraigned and entered a plea of not guilty. This was
expected. There apparently was no plea bargain on offer. Pre-trial
confinement was not sought by prosecutors. The judge tried to impose
separation of witnesses and defendants but even though Trump signed a
bond to that effect his word apparently means nothing. Both defendants
were seen by the media a meal together at a quick service restaurant and
appeared to be openly discussing \emph{something}.

Trump held a rally later that day at his property in Bedminster, New
Jersey. He apparently rambled on for half an hour. His references to
``communists'' was weird. He was acting like a CPSU party leader from
the bad old days of the Soviet Union who would drone on with endless
speeches. The speech did not act as an inciting event \emph{yet} as far
as can be seen but most of the people who would have been motivated to
commit violence are presently behind bars, I think.

Many of what he thought were defenses in his speech were instead utter
nonsense. He apparently made admissions against interest in the speech
that can be played back in front of the jury. A key problem is that it
is well-established after fifty years that a President does \emph{not}
have an absolute right to really anything once their time in office ends
beyond the rights they otherwise have as a citizen. Access to classified
documents and the ability to legally possess them is not a right
guaranteed to citizens at large and Comrade Citizen Trump is very much
in the wrong. If the documents were not declassified in 2021 by 12:00 PM
on January 20th then Trump lost any legal right to possess the
classified materials at that very moment unless he otherwise has a
security clearance nobody knows about or the current President granted
permission for Trump to see the papers. Trump has no clearance and
President Biden gave no permission.

Between the admissions against interest, the recordings the special
counsel's team has already secured, and the general insanity of what was
done\ldots this whole matter is best resolved by the Court. No document
custodian is going to look at the situation and state that they are able
to unequivocally certify that Trump met all appropriate security
standards in possessing such materials at the property in Florida. This
is all so unnecessary yet here we are.

Surprisingly the speech did not turn into an inciting event. We keep
getting closer to \emph{something} happening, it seems.
