Well, we will have interesting weather if
\href{http://web.archive.org/web/20230113013428/https://forecast.weather.gov/showsigwx.php?warnzone=OHZ089&warncounty=OHC007&firewxzone=OHZ089&local_place1=Ashtabula\%20OH&product1=Winter+Weather+Advisory&lat=41.8681&lon=-80.7877\#.Y8C1Kv7P02w}{the
Winter Weather Advisory stretching along the southern shoreline from the
western edge of Lorain County through Chautauqua County in New York
State} brings the goods. The Ashtabula County Emergency Management
Agency posted to \emph{its Facebook Page} about the situation. Sadly
there are no significant media outlets in-county that they could reach
out to that could carry their updates.

The four television stations in Cleveland \emph{do not agree} as to
possible snow impacts of the storm. None of them really provide any
clear resolution for Ashtabula County. This county is the largest in
terms of area in the state. It would be nice to not have so many
competing opinions.

This area is fertile ground for MAGA. When you can't even agree on
\emph{the weather} then it is not much further to go to the MAGA
madness. Building a common communications infrastructure helps build a
common identity and frankly Facebook \textbf{does not do that}.

The computer technology side of things is pretty much in order for
handling production. The problem right now is \emph{lighting} which
trickles down from not really have an ideal space to work in. I could
swap the camera for something with better light controls but that's a
completely different can of worms to open.

This isn't being set aside. I just have to clear some hurdles yet.
