My safety in Ashtabula County is becoming questionable. Despite calling
themselves Christians we have an extremely large group of idolatrous
people who think that Donald Trump is unjustly maligned and is being
persecuted by the government. These people are self-radicalizing thanks
to Facebook as they repeatedly amplify the erroneous notion that Donald
Trump had every right to do what he did with respect to the classified
materials and that it is unfair that Mike Pence and Joe Biden did not
get prosecuted.

As to Pence and Biden, they cooperated with the National Archives and
the Department of Justice. Them having the materials at all was
apparently truly accidental. We don't prosecute people for accidents.
Criminal intent is prosecuted.

Donald Trump did not cooperate with the National Archives and the
Department of Justice. That's why the forced entry to the property in
Florida had to take place. If he had truly cooperated then the search
pursuant to the warrant should not have found anything. Instead it found
materials Mr.~Trump had no legal right to possess.

The lies about declassification have not been helpful. For all Trump's
bloviating about standing orders to automatically declassify materials
we have a major problem of no copy of such an order existing.
Declassification by telepathy is not a thing under law either.
Declassification by waving a hand over materials is not a thing either.
Those statements fuel the charge under 18 USC 1001 for lying to federal
agents.

Donald Trump was trying to act like a supervillain and failed. What
makes things worse is that the Special Counsel's team got their hands on
a recording of Trump outright acting like a supervillain. He was
admitting on tape that he lost the 2020 race and also admitted that he
had no authority to have the documents in his possession.

This bodes ill.
