Well, it has leaked out that local law enforcement as well as
representatives of the federal law enforcement establishments
\href{https://web.archive.org/web/20230318002208/https://www.nbcnews.com/politics/donald-trump/law-enforcement-agencies-are-prepping-possible-trump-indictment-early-rcna75493}{are
gearing up for a possible indictment to drop in New York City in the
week ahead relative to Donald John Trump}. Since these would be
\emph{state court} charges he would not be able to pardon himself as to
these charges if he was elected President of the United States. He would
have to be Governor of New York state to issue the pardon and since he
is now legally a resident of Florida that option is precluded. Governor
Kathy Hochul may well issue fairly quickly the extradition warrant under
\href{https://web.archive.org/web/20230115185005/https://constitution.congress.gov/constitution/article-4/}{Article
IV, Section 2, Clause 2 of the United States Constitution}.

Why the worries about violence? Well, concerns were being raised in the
\emph{Los Angeles Times}
\href{https://web.archive.org/web/20220818231611/https://www.latimes.com/opinion/letters-to-the-editor/story/2022-07-26/trump-charged-jan-6-possible-civil-war}{last
year in July} as to him over possible charges about the US Capitol riot.
At a rally in Texas
\href{https://web.archive.org/web/20230307001022/https://www.huffpost.com/entry/trump-protests-prosecution_n_61f60c9ee4b02de5f51a0c4a}{Trump
himself was telling his followers that the prosecutors were villains
persecuting him}. Joe Walsh, a former member of the United States House
of Representatives,
\href{https://web.archive.org/web/20221230140433/https://www.newsweek.com/joe-walsh-warns-major-violence-if-donald-trump-indicted-january-6-capitol-riots-1725601}{made
remarks last July likeneing any indictment of Donald John Trump as being
akin to an indictment of a cult leader} that would probably lead to
fallout from the cultists.

Meanwhile, the former president has outright stated
\href{https://web.archive.org/web/20230315023902/https://news.yahoo.com/fox-news-edits-trump-saying-210420818.html}{that
he would have Ukraine surrender land to the Russian Federation} to end
the Russo-Ukrainian conflict. Yeah, I missed the discussion on MSNBC
\href{https://archive.org/details/MSNBCW_20230310_030000_The_Last_Word_With_Lawrence_ODonnell/start/2801/end/3248.5}{nine
days ago} but I don't have cable. I don't pay for
\href{https://en.wikipedia.org/wiki/Peacock_(streaming_service)}{Peacock}
and the only news from NBC that I watch is via
\href{https://web.archive.org/web/20230317135428/https://www.nbcnews.com/now}{NBC
News Now}.

All in all this is a volatile mix. The fellow wants to be a warlord. Was
the US Capitol riot our version of Germany's Beer Hall Putsch?

Rather than Florida Man, the prisoners on the Satellite of Love faced
their own \href{https://youtu.be/cW-5qrwsiOI}{Trumpy}.
