Am I great at slinging shell scripting? I feel doubtful about that.
Consider the following excerpt:

\begin{verbatim}
# Declare variables

DUB=$( date "+%A-%d-now.png")
WUB=$( date "+%A-%d-soon.png")

# Grab images from NOAA
curl -C - --retry-delay 3 --retry 5 --output $DUB "https://graphical.mdl.nws.noaa.gov/GraphicalNDFD.php?width=1920&timezone=EST&wfo=KCLE&element=wx&n=2"
curl -C - --retry-delay 3 --retry 5 --output $WUB "https://graphical.mdl.nws.noaa.gov/GraphicalNDFD.php?width=1920&timezone=EST&wfo=KCLE&element=wx&n=3"
\end{verbatim}

I don't have the logic working quite right here. In theory this
\emph{should} grab maps showing weather conditions from the perspective
of the National Weather Service forecast office in Cleveland. In
practice it is rather finicky and does not always return maps like it
should.

There is a \emph{separate} API for the National Digital Forecast
Database but it is a bit of a mess. Either I am missing something when I
follow the directions at
\url{https://digital.weather.gov/staticpages/mapservices.php} or there
is a step missing there.

Why worry about this? Well, I want to grab materials in a semi-automated
fashion to be able to put together the weather report videos for
\href{https://coyote.works/}{ELP Television}. The full script is not one
hundred percent stable as the NOAA server mixes production and
experimental data. There is still the push to get \emph{some production}
running so that we have \emph{some} programming locally.

At least this is a small part of the puzzle. Slowly but surely we're
getting there.
