Screw it, I was going to write about something else but I wound up
deleting it. It was for the best. If you read the backscroll on that
channel you read the backscroll on that channel. Just know that I am
quiet on that channel because I have been really, really busy with stuff
at the employer rather than trying to duck people.

\href{https://www.theincomparable.com/tpk/}{Total Party Kill} is the
best escapism that I can get at the moment. Frankly commuting an hour
each way to the work site in
\href{https://simple.wikipedia.org/w/index.php?title=Erie,_Pennsylvania&oldid=9061305}{Erie}
is hard. Random health goofiness hasn't helped either. Listening to Tony
Sindelar run games while I am driving on
\href{https://simple.wikipedia.org/w/index.php?title=Interstate_90&oldid=8969887}{Interstate
Route 90} and
\href{https://simple.wikipedia.org/w/index.php?title=Interstate_79&oldid=5516605}{Interstate
Route 79} helps keep me going on the long drives. I also listen to
programs from
\href{https://en.wikipedia.org/w/index.php?title=Big_Finish_Productions&oldid=1179492428}{Big
Finish Productions} quite a bit while on the road, too.

I have been looking at a
\href{https://www.drivethrurpg.com/product/232269/Mad-Magicks-of-the-Turned-God-A-Tiny-Dungeon-2e-Quickstart}{TinyD6
quickstart}. These are useful sorts of things. What that might lead to
is a different question, though. Additional escapism is the goal.

The world is looking really bleak this autumn. We'll all be needing some
escapism, I think.
