Via \href{https://electionlawblog.org/?p=134980}{a post} on the Election
Law Blog helmed by Rich Hasen, word comes from NBC News
\href{https://www.nbcnews.com/politics/justice-department/tucker-carlson-new-video-provided-speaker-mccarthy-falsely-depicts-jan-rcna73673?cid=sm_npd_nn_tw_ma}{that
Tucker Carlson is lying through using deceptively edited footage about
the events of January 6, 2021}. He has reportedly said that the people
attacking the capitol were \emph{peaceful} and used deceptive cuts of
the security footage to make it look like that. Who gave him the
footage? Speaker of the House Kevin McCarthy did! The linked article
from NBC quotes Senator Josh Hawley and Senator Chuck Grassley saying
that we should all look forward to further releases by Tucker Carlson
and that Mr.~Carlson will bring us the \textbf{ultimate} truth of the
matter.

Speaker McCarthy, Senator Hawley, and Senator Grassley are enemies of
reality. They're trying very hard to rewrite the history of that day
where all three of them were in mortal danger. Senator Grassley himself
was third in line to the presidency as President Pro Tempore of the
Senate and had to be just as protected as Speaker Nancy Pelosi was. We
were at serious risk of losing the first three people in the order of
succession to the presidency that day. Denying that that happened is to
deny reality.

Evan Prodromou recently asked in one of his infamous poll questions if
people were ``ready to run for it''. He was an expat and is now a
recently naturalized Canadian. He can look south and now not worry about
the craziness here.

People thinking about running north should
\href{https://www.canada.ca/en/immigration-refugees-citizenship/services/come-canada-tool.html}{probably
take the quiz offered by Immigration Canada} to see how they qualify to
do so, it at all. Things are getting scarier by the day here in America.
