After switching the hosting on this site away from Netlify to GitHub
Pages it is probably time for another miscellany of relatively brief
items. In no particular order:

\begin{itemize}
\tightlist
\item
  I no longer have anything hosted via Netlify now.

  \begin{itemize}
  \tightlist
  \item
    This blog was shifted off Netlify to GitHub Pages.\\
  \item
    The site for Erie Looking Productions was shifted to a Raspberry Pi
    Zero W 2 that is sitting in my basement that is exposed to the world
    using PageKite and a CNAME set up on the DNS for the domain name\\
  \item
    At one point this blog was going to live on the RPi Zero W 2 in
    addition to the Erie Looking Productions site but redoing the
    logistics of Jekyll was getting too fiddly.
  \end{itemize}
\item
  I have procured a Lenovo T480 to use on work taskings and it is now
  running Windows 11.\\
\item
  I have been having strange dreams. I blame
  \href{https://tubitv.com/movies/712905/bikini-hackers?start=false}{\emph{Bikini
  Hackers}}.
\item
  There is another round of appointments coming up with medical
  practitioners that I haven't met before.

  \begin{itemize}
  \tightlist
  \item
    I'll be meeting a dietitian for the first time on Thursday.
  \item
    I'll be meeting a particular neurologist for the first time on the
    following Monday.
  \item
    The care odyssey continues and the answers that we're finding are
    frankly resulting in even more questions.
  \item
    Rare conditions are not fun things. Second opinions aren't things
    you can simply seek. First opinions by themselves probably could
    lead to articles in medical journals!
  \end{itemize}
\item
  Efforts continue relative to finding somewhere else to live. We've
  lost our last local movie theater. When the local Walmart closes down
  it would be quite fair to say my area would be on an accelerated
  course towards being a ghost town.
\item
  \emph{Colossus: The Forbin Project} is a very weird movie. I see now
  why it is a touchstone that comes up in riffing by Frank Conniff.
\item
  Class is going to look different in the fall semester as we're
  ditching the textbook from Pearson and will be going with something
  different. My current group really, really do not like the Pearson
  text.
\item
  Some things need to get off the drawing board as the world around me
  deteriorates.
\end{itemize}
