I tag plenty of things in my RSS reader with stars. It is a good idea to
review it from time to time. NetNewsWire doesn't provide a simple way to
dump all the bookmarks anyhow.

\href{https://www.avclub.com/cbs-orders-pilot-of-matlock-reboot-starring-kathy-bates-1850057294}{The
AV Club: ``CBS orders pilot of that Kathy Bates-led Matlock reboot we've
been praying for''}

Could we please make \emph{something} new and original? I grew up around
Matlock being on the first time around starring Andy Griffith. American
broadcast television would be better with more things like
\href{https://en.wikipedia.org/w/index.php?title=Almost_Paradise_(TV_series)&oldid=1136391664}{\emph{Almost
Paradise}} on the air.

\href{https://variety.com/2023/tv/news/dr-phil-talk-show-end-oprah-cbs-1235508811/}{Variety:
``\,`Dr.~Phil' Talk Show to End in Spring After 21 Seasons''}

I'm surprised the show has been on that long. This will leave a hole in
the syndicated television show landscape.

\href{https://variety.com/2023/digital/news/peacock-ends-free-tier-nbcuniversal-1235508588/}{Variety:
``NBCUniversal Shuts Off Peacock Free Tier for New Users''}

That's not a good sign. I currently have a ``free tier'' account.
Nothing on the service interests me enough to pay for a service I won't
really watch.

\href{https://web.archive.org/web/20230201053754/https://fox8.com/news/local-high-school-musical-abruptly-halted-deemed-vulgar/}{Fox
8 Cleveland WJW: ``Local high school musical abruptly halted, deemed
`vulgar'\,''}

The musical in question is ``The 25th Annual Putnam County Spelling
Bee'' which was originally released in 2005. It is really sad that
something like this happened in Middlefield. It is uncalled for.

\href{https://web.archive.org/web/20230201054113/https://radioinsight.com/headlines/248153/skyview-notifies-affiliates-of-unauthorized-it-access-affecting-program-delivery/}{RadioInsight:
``Skyview Notifies Affiliates Of `Unauthorized IT Access' Affecting
Program Delivery''}

Well, that would explain why the evening television news on broadcast
has been looking a little weird lately.

\href{https://web.archive.org/web/20230201054252/https://fox8.com/news/i-team/ohio-educators-condemn-alleged-nazi-themed-home-schooling-in-upper-sandusky/}{Fox
8 Cleveland WJW: ``Ohio educators condemn alleged Nazi-themed
home-schooling in Upper Sandusky''}

I'm still in shock at the situation. We need a thorough house cleaning
here in Ohio. Yes, I know there are bad things happening elsewhere in
the USA. Metaphorically speaking, you can't respond to other people's
houses being on fire if your own house is on fire too. We have some huge
issues here in Ohio that we try to just ignore.

\href{https://religionunplugged.com/news/2023/1/23/analysis-data-shows-democrats-increasingly-becoming-the-party-of-non-religious-voters}{Religion
Unplugged: ``Why Democrats Are Less Religious Than Republicans''}

This piece goes in unexpected directions.

\href{https://variety.com/2023/biz/news/australia-streaming-quotas-1235506165/}{Variety:
``Australia to Introduce Streaming Quotas by Mid-2024''}

With the lack of original scripted content here in the USA perhaps we
should import some of this mandated Australian content to show here? The
CW started doing that to a limited extent by importing the show
\href{https://www.imdb.com/title/tt13751472/}{``Bump''}. Other imports
include
\href{https://www.imdb.com/title/tt11873484/?ref_=nv_sr_srsg_0}{Family
Law} and
\href{https://www.imdb.com/title/tt8593252/?ref_=nv_sr_srsg_0}{Coroner}
but those two are from Canada.

\href{https://drewdevault.com/2023/01/30/2023-01-30-Should-private-platforms-engage-in-censorship.html}{Drew
DeVault's Blog: ``Should private platforms engage in censorship?''}

I'm not satisfied with this post. The topic is very messy so I don't
have an immediate argument in opposition, alas.

\href{https://www.latimes.com/politics/story/2023-01-27/school-librarians-vilified-as-the-arm-of-satan-in-book-banning-wars}{Los
Angeles Times: ``School librarians vilified as the `arm of Satan' in
book-banning wars''}

I'm waiting for the Facebook invites to ``holy book burnings''. They're
inevitable as this continues to devolve. With the madness accelerating
like this it may well be time to take stock as to the viability of
remaining in CONUS.

\href{https://electionlawblog.org/?p=134506}{Election Law Blog:
``Trump's Evolution in Social-Media Exile: More QAnon, More Extremes''}

Not good.

\href{https://variety.com/2023/artisans/news/missing-crew-iphone-facetime-footage-easter-eggs-1235492655/}{Variety:
``\,`Missing' Crew Explains How They Told a Thriller Almost Entirely
Using FaceTime, iPhone and Ring Footage''}

This is awesome.

\href{https://www.techdirt.com/2023/01/27/biden-administration-declares-war-on-the-internet-clears-path-for-offensive-hacking-efforts-by-federal-agencies/}{Techdirt:
``Biden Administration Declares War On The Internet, Clears Path For
Offensive Hacking Efforts By Federal Agencies''}

Just think about the changes being made by the Biden administration
being wielded by a second Trump administration. What could possibly go
wrong?

\href{https://arstechnica.com/?p=1912543}{Ars Technica: ``DirecTV dumps
Newsmax instead of paying new fee, drawing Republican outrage''}

When your linear network is so terrible that you have such low
viewership that there is no price DirecTV could justify to pay for
carriage\ldots{}

\href{https://hackaday.com/2023/01/25/secure-lora-mesh-communication-network/}{Hackaday:
``Secure LoRa Mesh Communication Network''}

I need to review this again. Infrastructure in my local area is
increasingly fragile.

\href{https://theconversation.com/ozempic-helps-people-lose-weight-but-who-should-be-able-to-use-it-196794}{The
Conversation: ``Ozempic helps people lose weight. But who should be able
to use it?''}

Read the whole thing. It isn't as easy of a matter as it may seem at
first glance.
