I got up feeling not all that well this morning. I was supposed to be
supervising the slideshow using
\href{http://web.archive.org/web/20230127224925/https://renewedvision.com/propresenter/}{ProPresenter}
at church. Someone wound up having to cover me as I stayed home. Dad
made it to church while Mom stayed home with me.

While we were watching the live feed from church we got a call. My one
sister who works in Mentor
\href{https://en.wikipedia.org/w/index.php?title=Mentor,_Ohio&oldid=1130934184}{(yes,
that is literally its name)} was having a medical crisis. I grabbed my
go bag, got in the car with Mom, and we started the hard drive west from
Ashtabula to Mentor. Once we picked up that sister we then continued the
drive to
\href{https://my.clevelandclinic.org/locations/hillcrest-hospital}{Hillcrest
Hospital} for the emergency department. The sister's problem happened
once already and the nice people at
\href{https://www.acmchealth.org/}{Ashtabula County Medical Center's}
emergency department simply blew it off as being nothing. We're getting
a second opinion since it is happening again.

At this point I am sitting in the cafeteria in the basement here in the
hospital. Mom and the sister are back in the waiting room after seeing
triage. It will be a minimum of an hour before we have an initial
diagnosis of what is going on in this situation.

No, I don't feel good at the moment. I wasn't expecting to make a run to
Cleveland like this. I am across the street from
\href{https://www.microcenter.com/site/stores/mayfield-heights.aspx}{MicroCenter}
so I suppose I can visit them today while I am down here.
