On the about page for this page you'll see this updated languages:

\begin{quote}
\emph{Stephen's creative endeavors can be supported financially via
\href{https://ko-fi.com/smkellat}{Ko-Fi}. Support is encouraged to allow
him to be able to work on creative endeavors such as writing fiction,
creating things using LaTeX, and returning more to podcasting.
Podcasting as just a side hustle is rough.}
\end{quote}

It is a fair question to ask \emph{why} that would show up. Simply put,
the commute is getting to me. Yes, I only do the commute two days out of
the work. It is still quite a drive. The drive is simply getting to me.

Currently I have been writing up a tabletop exercise for use in class
Monday. I like this situation as it frankly will be an original tabletop
game for the students to work in. Yes, this is partly
\href{https://eric.ed.gov/?qt=game&ts=on&td=on&ti=Gamification}{gamification
of learning}. The scenario will deal with
\href{https://www.cisa.gov/topics/critical-infrastructure-security-and-resilience/critical-infrastructure-sectors/water-and-wastewater-sector}{water
and wastewater systems} and will keep in mind what happened
\href{https://www.cbsnews.com/pittsburgh/news/municipal-water-authority-of-aliquippa-hacked-iranian-backed-cyber-group/}{in
Aliquippa}. CISA issued an alert on this in
\href{https://www.cisa.gov/news-events/cybersecurity-advisories/aa21-287a}{2021}
and again
\href{https://www.cisa.gov/news-events/cybersecurity-advisories/aa23-335a}{on
December 1st this year}. Even US EPA
\href{https://www.epa.gov/waterresilience/epa-cybersecurity-water-sector}{is
issuing alerts on this}.

The thing is that this is all \emph{creative work}. I enjoy doing this
and apparently it has practical utility somewhere. The local job market,
such as we still manage to have one, is dominated by openings in the
health care sector and not much else. You know your local economy is
screwy when even the temp agencies are having problems staying open.

Right now I am not in a position to be able to sell my house and just
move to Erie. There are some major countervailing factors that push me
towards staying in northeast Ohio near University Hospitals of Cleveland
and Cleveland Clinic. If I didn't have access to them I would then need
to turn to a provider in Philadelphia for appropriate care followed by a
provider in Boston.

If I had the backing I wouldn't have to worry about costs too much. The
library is talking about me running a TTRPG program series in 2024. I'm
still trying to build a streaming channel on no budget at all. I've been
neglecting my writing and need to do more of it. Creative output seems
to be the plan shaping up for 2024.

My life takes unexpected twists and turns. Heck, I could very well not
be living in the USA in 2025 with the way things are trending right now
politically. I do know that I gotta change things up a little bit.
