In no particular order:

\begin{itemize}
\tightlist
\item
  Production for the vodcast project has hit a hopefully temporary snag.
  Further efforts are required to get it back on track.

  \begin{itemize}
  \tightlist
  \item
    It is \emph{not} planned presently to have me in front of the
    camera.
  \item
    Somebody has to operate all the gear for video production and I'm
    the only one with enough expertise.
  \item
    I worked on a cablecast PEG channel back in the very late 20th
    century as a college freshman. I feel old at times.
  \end{itemize}
\item
  The roller coaster weather is not helping my daily health. None of us
  at home feel all that well with weather conditions oscillating day to
  day.
\item
  The wait for the test results for Mom and Dad continues. I'll be very
  curious as to what comes back. Depending upon the results they get my
  diagnostics appointment in early February might have an effectively
  pre-determined outcome. Of course, there is a chance that there is
  weirdness in play and their results will mean I'll have things to
  worry about still.
\item
  People are getting angrier and angrier on the roads locally. I'm
  getting scared of driving as frankly too many people are ignoring
  traffic laws and are instead following ``might makes right'' as they
  drive.

  \begin{itemize}
  \tightlist
  \item
    No, I can't up and leave just yet. Too much testing is still in play
    yet.
  \item
    Depending upon how testing goes I would have to think long and hard
    about moving away from nationally-ranked top hospitals in Cleveland.
  \item
    That Cleveland Clinic is a research leader globally in what all the
    testing is about is a good thing even though it may lead to my being
    tied down hard to this area.
  \end{itemize}
\item
  Two desktop computers that have been limping along here at home are
  likely to be stripped of suitable parts to build a nice tower. Would
  such a thing need multiple optical drives? When working with video
  like this the answer is yes. There is also an IDE/SATA 2.5''
  multi-type memory card reader in one of the machines that could be
  transplanted to a tower. The SSDs in both boxes could be wiped and
  reused, I think. The IEEE1394 port card could be shifted over even. I
  just need a tower case, power supply, motherboard with processor,
  suitable video card\ldots{}
\end{itemize}
