In no particular order:

\begin{itemize}
\tightlist
\item
  The latest episode of
  \href{https://www.paramountplus.com/shows/star-trek-picard/}{\emph{Star
  Trek Picard}} was good. What would be really good would be to instead
  have a sort of buddy cop show with just Worf and Raffi.\\
\item
  COVID-19
  \href{https://covid.cdc.gov/covid-data-tracker/\#county-view?list_select_state=Ohio&data-type=CommunityLevels&list_select_county=39007}{test
  positivity in Ashtabula County} is now just under 15\%. This is
  getting ridiculous.
\item
  Big Finish has some interesting
  \href{https://www.bigfinish.com/collections/v/last-chance-on-cd?sort_ordering=price_asc&search_product_type=&search_availability=all}{clearance
  sale items on CD} in terms of good stories.
\item
  I wound up looking at a
  \href{https://www.gottagrooverecords.com/home/ggr-record-builder/}{vendor
  for pressing custom records} and remembered how expensive such things
  happen to be.
\item
  Thursday was a
  \href{https://www.starbeacon.com/news/ashtabula-emergency-workers-busy-on-thursday-afternoon/article_9864c008-c436-11ed-a6dc-2fe459576e8a.html}{very
  bad day} in Ashtabula City. I drove past the accident where the
  tractor-trailer rig collided with the Dollar General store's outdoor
  curbside sign. The pole that the sign happened to be affixed to went
  through the engine block. To clean that mess up they had to first
  detach and remove the trailer then separate the rig from the pole. The
  engine was pretty much destroyed so it was an insurance write-off.
\item
  I will \textbf{not} be attending any St.~Patrick's Day parades. We
  don't have any in Ashtabula County that I'm aware of. If there are any
  they're being kept secret or were announced in hidden corners of
  Facebook.
\item
  After the
  \href{https://blogs.microsoft.com/blog/2023/03/16/introducing-microsoft-365-copilot-your-copilot-for-work/}{Microsoft
  365 Copilot presentation Thursday}, I want to shift as much as
  possible to Nextcloud. I am just creeped out by this thing and am not
  happy with where it goes.
\item
  I need to remember to catch \href{https://swradiogram.net/}{Shortwave
  Radiogram} tomorrow.
\item
  Eventually an \href{https://www.sdrplay.com/rsp1a/}{RSP1A} will be
  procured to set up automated monitoring of certain broadcasts such as
  \href{https://www.weather.gov/marine/uscg_broadcasts}{Sector Buffalo}
  on VHF as well as \href{https://www.weather.gov/marine/marsh}{charts
  out of Boston}.
\item
  Setting up a streaming television station in Ashtabula County is
  looking like a proposition that requires a budget nearing a minimum of
  a quarter million dollars. In short it is likely impossible in the
  current situation to launch such a thing.\\
\item
  The current episode of
  \href{https://www.electricnow.tv/shows/ark/season/1/episode/7}{\emph{The
  Ark}} was really good. I don't get why people are slagging it off in
  online reviews. This is a wonderful show.
\item
  I am really getting into the
  \href{https://critrole.com}{\emph{Critical Role}} audio podcast of the
  games which can be subscribed to using
  \href{https://feeds.simplecast.com/LXz4Q9rJ}{this RSS feed}.
\item
  Further events will ensue\ldots{}
\end{itemize}
