In no particular order:

\begin{itemize}
\tightlist
\item
  I need to move.

  \begin{itemize}
  \tightlist
  \item
    Sunday night sounded like World War III in the neighborhood. The
    firing off of fireworks is \textbf{banned} within city limits but
    people really don't care any more.
  \item
    We have multiple economic aspects locally entering an adverse spiral
    situation.
  \item
    There are even more Confederate battle flags popping up in
    unexpected places locally

    \begin{itemize}
    \tightlist
    \item
      This area was a major terminus of the Underground Railroad!
    \item
      The new
      \href{https://ohiohistorycentral.org/w/Copperheads}{copperheads}
      appear to overlook history like
      \href{https://ohiohistorycentral.org/w/Morgan\%27s_Raid}{Morgan's
      Raid}
    \end{itemize}
  \end{itemize}
\item
  Building a standalone streaming channel is hard

  \begin{itemize}
  \tightlist
  \item
    The regular installer for
    \href{https://openbroadcaster.com/}{OpenBroadcaster} seems to be
    borked
  \item
    I've been looking for a suitable broadcast automation solution for
    streaming video on a somewhat constant flow

    \begin{itemize}
    \tightlist
    \item
      There needs to be a bit more than a single live program flowing
    \item
      I want to have a ``broadcast day'' that can be programmed
    \item
      I recognize that setting up my own instance of
      \href{https://owncast.online/}{owncast} for doing something like
      this would be needed
    \end{itemize}
  \item
    I don't have a suitable fiscal structure in place to support such an
    effort

    \begin{itemize}
    \tightlist
    \item
      A sole proprietorship isn't the safest thing to do with the
      amounts of money involved
    \item
      It takes time to get the paperwork cleared to set up an Ohio LLC
    \item
      I would have to hunt around to find a decent bank to use for
      corporate treasury services
    \item
      These are all predicate steps to launching any sort of
      crowd-funding effort
    \end{itemize}
  \item
    Our local daily newspaper owned by
    \href{https://www.cnhi.com/}{CNHI} is becoming a ghost of its former
    self

    \begin{itemize}
    \tightlist
    \item
      There seems to be no easily understandable reason why it is still
      being published
    \item
      Averaging only 12-16 broadsheet pages per issue is not a plan to
      stay in business let alone remain a ``newspaper of general
      circulation'' under Ohio legal ad standards
    \item
      The only other newspapers in the county are the regional weeklies
      that share the same editor and almost all the same content
    \item
      As this isn't getting better we need to do \emph{something}
    \end{itemize}
  \item
    Commercial real estate is a nightmare here that has held this back
    and I still don't have a good answer to it
  \end{itemize}
\item
  Work continues

  \begin{itemize}
  \tightlist
  \item
    The commute is still rough
  \item
    As legislation moves through its steps in the statehouse in
    Columbus, doing this sort of work tasking in Ohio is increasingly
    not in the cards
  \end{itemize}
\item
  Church life continues

  \begin{itemize}
  \tightlist
  \item
    We're still streaming and people are still watching
  \item
    I'm still there at Geneva Church of Christ
  \item
    As much as we may not like it, we've come to accept that in an area
    with as bad of a set of health outcomes as Ashtabula County there
    will be a wider range of ``shut ins'' with nasty health issues who
    won't be able to rejoin us in the sanctuary in the current
    environment
  \end{itemize}
\item
  I shot my mouth off about starting an actual play podcast of Linux
  world people playing a suitable TTRPG and now I'm wondering how I can
  make that happen
\end{itemize}

Your Reading Homework:

O'Gara, A. (2023). \emph{Hoodwinked: Deception and Cooperation in a
Text-Based Game for Language Models} (arXiv:2308.01404). arXiv.
\url{https://doi.org/10.48550/arXiv.2308.01404}\\
Park, P. S., \& Goldstein, S. (2023, September 4). \emph{AI systems have
learned how to deceive humans. What does that mean for our future?} The
Conversation.
\url{http://theconversation.com/ai-systems-have-learned-how-to-deceive-humans-what-does-that-mean-for-our-future-212197}
