In no particular order:

\begin{itemize}
\tightlist
\item
  I got through the procedure on Thursday. It took longer for the
  anesthesia to wear off than for the diagnostic procedure to actually
  take place. The picture being painted by all these tests and
  procedures frankly is one where the big questions don't really have
  readily known answers.\\
\item
  Apparently the power move now is to
  \href{https://web.archive.org/web/20230415081034/https://www.newsweek.com/texas-library-may-face-elimination-weeks-after-banned-books-return-1793510}{just
  remove all funding and shutter libraries} if you can't ban books in
  them. One Texas county thinks that is a swell idea.
\item
  Missouri's state legislature decided
  \href{https://web.archive.org/web/20230415103204/https://www.salon.com/2023/04/12/missouri-state-vote-to-defund-public-libraries_partner/}{it
  wants to get in on the game of terminating the existence of libraries}
  if books inside them can't be banned.\\
\item
  I didn't know that there is a version of Windows
  \href{https://www.kotaku.com.au/2023/04/microsoft-devs-built-a-basic-version-of-windows-optimised-for-steam-deck/}{optimized
  for the Steam Deck}. Of course, I don't have one of those things. I'll
  need to see if there's any call for me to actually procure one some
  day.
\item
  Apparently
  \href{https://www.giantfreakinrobot.com/ent/brie-larson-marvels-bra.html}{the
  fashion of Brie Larson} merits blog posts?\\
\item
  Why bother with dark alleys when you can just meet on Discord if
  you're a spy? Apparently
  \href{https://www.techspot.com/news/98313-microsoft-warns-russian-agents-trying-infiltrate-gaming-communities.html}{Microsoft's
  finding that that is exactly what is happening}.
\item
  I'm very happy to see that
  \href{https://web.archive.org/web/20230415094020/https://variety.com/2023/tv/news/the-ark-renewed-season-2-syfy-1235580978/}{\emph{The
  Ark} was given a second sesaon order}. I like that show.
\item
  Eventually I'll get a better grasp on what's going on this strange
  world I'm living in. There's just way too much weirdness at the
  moment.
\end{itemize}
