Tuesday saw me pushing ahead with the podcasting plan. Edits and
adjustments wwere me to the \href{https://69admins.com}{69 Admins} site.
Why that domain name? Well, it was mentioned once in the
\href{https://latenightlinux.com/chatter}{Late Night Linux channel on
Telegram} and I snagged it since it was unassigned. Even with the
efforts of a full sixty nine administrators you could not get the
broadband situation in this county fixed, alas. I know what the meme
implication of the name is \emph{and I do not care}.

Everything is set up to the extent that I can do so on
\href{https://acast.com/}{Acast}. The album art was created using Apple
Keynote and some pieces from OpenClipArt. The working podcast
description states:

\begin{quote}
\emph{From the south shores of Lake Erie comes a look at cutting the
cord to take advantage of streaming television. Taking advantage of
streaming television is a bit different from a rural perspective. In
this shot cast we'll be talking hints and tips to enjoy the TV streamers
while living in places where access to the Internet may not be the
greatest.}
\end{quote}

The target is to keep episode lengths at or under a limit of \textbf{ten
minutes}. The intended audience initially is folks in the Ashtabula area
so it is not like long rounds of exposition and pontification would be
beneficial. Even ten minutes might be pushing my luck.

Scripting is the next thing to be doing before we can get down to
recording. A goal will be to get a trailer posted as soon as possible. I
might even have that accomplished before the end of March if all goes
well.
