I've been watching Evan's threads out in ActivityPub-land about
authoritarianism and the bad situation we're finding ourselves in. I
approach the authoritarian question from a different angle. Our local
daily newspaper is fading away. The consolidated ``weekend edition''
this weekend had its body of local news articles written mostly by just
one reporter. That's not sustainable.

They've got the open reporter position advertised locally once again.
The owners of the paper, CNHI, are not advertising the position
nationally. It is only being advertised through a single small
classified ad in the impacted newspaper. It has been advertised for
weeks without any apparent success.

What does this result in? Well, local government goes unreported on.
Local events go unreported on. There is no ``citizen journalism''
locally. The local rumor-monger groups on Facebook are full of
propaganda and active measures originating from hostile powers.

This shows up as an explicit problem when it comes to the primary
election coming up in 2024. Yes, Ohio is a ``Super Tuesday'' state which
means our primary is moved from its usual spot in May to a weird spot in
March. That made a ton of elected positions \emph{uncontested}. In many
cases only the incumbent managed to file their petition papers by the
December 20th deadline and they wound up with no competitors in their
party primary. To make matters worse, the party primary for the party
opposed to the incumbent in far too many cases had \emph{nobody file at
all}. This means that the two county commissioners up for re-election
will not even have to campaign or face the voters if there is no
independent candidate filing made by March 18th.

When your news media dies off and people become numb to the world around
them because they don't understand what's going on, authoritarianism has
quite an opening to take root. Authoritarians provide answers about a
complicated and chaotic world when nobody else is around. They provide
that feeling of safety when people feel alone and disconnected as we've
seen with QAnon's rise and with the resurrection of the Sovereign
Citizen Movement.

Keeping a civil society running requires work. It doesn't operate on its
own. Right now nobody wants to invest in it as there is a big push to
try to let computers handle things and to delegate to AI as much as
possible. Society still needs a human touch and that lack is a big part
of what is driving this decline.
