It looks like the SAG-AFTRA strike isn't ending any time soon. I
lamented that on the
\href{https://69admins.com/2023/episode-14.html}{most recent episode of
69 Admins} as I then put that show on its ``hiatus for the holidays''.
Frankly reruns are getting tiresome. Family is getting tired of it too.

Within the scope of the contracts and avoiding being a scab, it would be
possible to proceed with starting an actual play tabletop role playing
game show. We're at the point where this could be done with folks
joining in via video call. It could be a Linux community members group
participating, for example.

I would want to start with
\href{http://www.memento-mori.com/pdf/parsely-pdf}{Parsely}. I went
through one of the free adventures with one of my classes as an exercise
during their ``problem solving'' module and that went quite well. The
folks at The Incomparable
\href{https://www.theincomparable.com/gameshow/actioncastle/}{have a
range of podcast episodes illuminating some of these adventures} and how
some tech people approach them. My copy of the actual print book is
coming later this week.

The nice thing is that they're one shots and the level of investment
required is low. They're somewhat silly, too. They are things that could
be reasonably accomplished within a couple hours.

I haven't decided whether I would want to do this via video program or
audio podcast. It seems like the 2100-2200 UTC time slot seems to fit
the general notions of time when people will be awake to participate
even if they were joining in from the UK, Western Europe, or Australia.
Keeping things short initially would allow for these sorts of things to
be recorded.

The best outlets for new non-news, non-sports programming that I have
found lately are still \href{https://dumb-industries.com/}{Dumb
Industries} and \href{https://critrole.com/}{Critical Role}. I'm not
ready to go down the road of movie riffing. Having persons from the
Linux world doing TTRPG stuff would be kinda neat for an odd sort of
audience, I suppose.

Eventually I might find a production partner to make this happen. Right
now I am busy with the employer. I definitely cannot be a ``one man
band'' to pull off something like this.
