In no particular order:

\begin{itemize}
\tightlist
\item
  Apparently I will be preaching in February. Topic is to be determined.
  We don't even have a theme for the month yet!
\item
  We'll be doing a sunrise service for Easter. This will be interesting.
\item
  Work continues as to how to build up a local streaming television
  service. We have plenty of talent and experience locally in Ashtabula
  County. We lack \emph{funding} and \emph{production space}.
\item
  We've been having intermittent network failures in the local
  broadband.

  \begin{itemize}
  \tightlist
  \item
    This hasn't been confined to just Windstream.
  \item
    Even my mobile broadband over the air with AT\&T has been having
    trouble locally.
  \item
    This hasn't made much sense.

    \begin{itemize}
    \tightlist
    \item
      Generally the infrrastructure has been working okay locally
    \item
      We're getting into winter collapses through lack of attention, it
      seems
    \end{itemize}
  \item
    Building for contingency plans is probably a good idea

    \begin{itemize}
    \tightlist
    \item
      I do suppose I need to do better in monitoring
      \href{https://www.weather.gov/marine/uscg_broadcasts}{the 9th
      District USCG marine weather broadcast} and the
      \href{https://ocean.weather.gov/shtml/atlsch.php}{various NOAA
      charts being transmitted by radio station NMF in Boston}

      \begin{itemize}
      \tightlist
      \item
        Reception of the ``Cleveland-area'' NOAA Weather Radio
        transmitter is rather rough
        \href{https://www.weather.gov/nwr/sites?site=KHB59}{based upon
        its coverage map} as it doesn't really cover Ashtabula
      \item
        Reception of the NWR transmitter in Erie is easier
        \href{https://www.weather.gov/nwr/sites?site=KEC58}{according to
        its coverage map}
      \end{itemize}
    \item
      At the very least I \emph{can} ensure reception of weather data is
      doable.
    \item
      Yeah, I'll need to take a harder look at
      \href{https://www.complete.org/building-an-asynchronous-internet-optional-instant-messaging-system/}{John
      Goerzen's idea for ``Building an Asynchronous, Internet-Optional
      Instant Messaging System''}

      \begin{itemize}
      \tightlist
      \item
        This means messing with
        \href{https://www.complete.org/lora/}{LoRa} potentially
      \item
        The addition of FRS band radios in the house shows that we
        already have some
        \href{https://www.complete.org/tools-for-communicating-offline-and-in-difficult-circumstances/}{``Tools
        for Communicating Offline and in Difficult Circumstances''}
      \item
        I may have to look at the use of
        \href{https://www.complete.org/yggdrasil/}{Yggradsil} too
      \end{itemize}
    \end{itemize}
  \end{itemize}
\item
  Waiting on the medical testing news is getting trying.

  \begin{itemize}
  \tightlist
  \item
    Plans for ife are on hold until tests are back.
  \item
    Results from tests could change the course of life decisions,
    unfortunately.
  \item
    While I am fortunate that there are world class doctors at Cleveland
    Clinic and University Hospitals of Cleveland, the need to be near
    them keeps me tethered to northeast Ohio. When some of those doctors
    are leading experts in the world on issues that are of possibly
    vital importance to me frankly I can't leave the area.
  \item
    I'm not sure where I'd relocate to at this point. Toronto has
    satellite facilities of Cleveland Clinic there. There are also
    satellite facilities in Abu Dhabi and the capital of the United
    Kingdom. CCF focuses on being a global powerhouse for medical care.
  \end{itemize}
\item
  I've paused the dating app and canceled the subscription

  \begin{itemize}
  \tightlist
  \item
    There were no viable hits in it
  \item
    The only responses I got were from women \emph{located in Canada}
  \item
    It just bothered me greatly that I could not get the time of day
    from anybody in northeast Ohio or northwest Pennsylvania but yet
    could match with people in southwest Ontario
  \item
    The app is based on a radius \emph{as the crow flies}. Even at a
    \textbf{50 miles} setting it would still bring in part of
    southwestern Ontario in addition to northeastern Ohio and
    northwestern Pennsylvania.
  \item
    Once I pick six possibilities to try my luck with next, I'll roll
    the dice with \href{https://www.pcalc.com/dice/}{Dice by PCalc} and
    see where random chance leads me in terms of picking a different
    dating app to try.
  \end{itemize}
\item
  What a strange world we live in these days\ldots{}
\end{itemize}
