This is another miscellany of various items. In no particular order:

\begin{itemize}
\tightlist
\item
  Thanks to \href{https://www.primepremiere.amazon/}{Prime Premiere} I
  went down to Valley View to watch in an actual movie theater the
  premiere of
  \href{https://www.amazon.com/Daisy-Jones-Six-Teaser/dp/B0B8NS22S2/}{Daisy
  Jones and the Six}. The episodes of the show that were shown were
  interesting. Having seen Imogen Waterhouse in
  \href{https://www.electricnow.tv/node/295}{The Outpost} it was very
  strange to see her older sister Suki in something. They look very
  alike although Suki is taller than Imogen. Suki plays the role of a
  keyboardist in \emph{Daisy Jones}. Imogen was merely the queen of the
  realm in \emph{The Outpost}.
\item
  We are enjoying \href{https://www.electricnow.tv/shows/ark}{\emph{The
  Ark}} courtesy Electric Now at home. It is a great show. I was
  \textbf{not} going to sign up for Peacock just to be able to see the
  show via SyFy. I'd much rather pay the producers directly.
\item
  I am going to be spending time researching
  \href{https://flcdatacenter.com/}{prevailing wage rates} for a variety
  of jobs. I know people locally have very skewed perceptions as to
  value, price, and cost. In planning to build a streaming video
  operations I would end up having to pay prevailing market rates
  \emph{at a minimum} to recruit staff. If anything I would have a
  premium on the prevailing rates as this area would be considered a
  hardship station. Average hourly pay for a cameraman in the northeast
  Ohio market is USD\$20.22. There is research to be done.
\item
  The \emph{Star Beacon} is getting even thinner. It is now averaging
  two sections of six broadsheet pages each. The next step down from
  that would be to produce only a single section of eight pages. From
  there it could collapse further to a single section of only four
  pages. The problem with these shrinking print editions is that there
  is no concurrent increase in online material. Output is down overall
  at the title. I don't know what CNHI is up to but we'll be lucky if
  the \emph{Beacon} survives the year.
\item
  The dating project has been left by the wayside for the time being. As
  much as I want to pursue it I have let it slip in the priorities. It
  will be pursued again at some point in the year ahead.
\item
  No deal in sight on the federal government's debt ceiling means that I
  have to start being very careful in how I schedule things. Nothing
  major should be scheduled after June 5th for the time being. That's
  simply being on the safe side right now. If the federal budget breaks
  I don't want to be caught in a mess yet again. I still have not so
  happy memories of the 35 day shutdown that kicked off in 2018.
\end{itemize}
