In no particular order:

\begin{itemize}
\tightlist
\item
  It looks like the first proper episode of
  \href{https://69admins.com/}{69 Admins} will be recorded soon for
  release on April 15th.\\
\item
  Learning about
  \href{https://www.edbrowse.org/usersguide.html}{edbrowse} seems to be
  an item to consider.\\
\item
  I'm not looking forward to the outpatient procedures coming up in a
  few days. They're not exactly the most comfortable things to have to
  go through.

  \begin{itemize}
  \tightlist
  \item
    There's still a rather large amount of diagnostic appointments this
    month.
  \item
    The appointment with the MD who is acting as ``quarterback'' isn't
    until May.
  \item
    What test results exist already are not exactly the simplest things
    to process. Then again, these are the fringes of known medical
    science that are being explored.
  \end{itemize}
\item
  Either UVB-76 is breaking down
  \href{https://hackaday.com/2023/04/08/russias-new-mystery-shortwave-station/}{or
  something is shifting for the worse}
\item
  I have to push work ahead on how to relocate to the United Kingdom
  somewhere near the University of Southhampton. Why there? There is a
  particular specialist there who collaborates with the specialists in
  Cleveland that I need to consult with. If I had to make a run for it
  that would be one way to ensure continuity of care adequately.

  \begin{itemize}
  \tightlist
  \item
    Melbourne in Australia would be a second option.
  \item
    Italy would be another option except I don't speak Italian.
  \item
    It still feels weird that the top world authorities in something
    would be based in Cleveland, Ohio.
  \end{itemize}
\item
  Once the current primary election concludes and is canvassed it will
  show me as having ``crossed the aisle''. This is intentional.
  Sometimes you have to walk away from madness.
\item
  Eventually more will be written but that will be saved for another
  time.
\end{itemize}
