There are folks becoming depressed with Biden's chances and are trying
to steel themselves for the coming Trump madness. Resistance is a bit of
a conundrum in circumstances like these. After all, how do you face a
powerful federal executive branch that is lawless and unable to be
reined in?

A family member jokingly asked me if I was going to be setting up a
paramilitary training camp somewhere. I laughed and said no. Teaching
how to read, think, and live in this crazy world is very important.
Doing that in a camp setting \emph{could} work and is probably the most
dangerous thing anyone could possibly do. The most dangerous thing to a
maladministration like Trump is proposing would be to have an educated
populace that is fit, healthy, able to think, and able to recognize that
\emph{none of this} is normal.

Would it cost money? You betcha!

Would it be difficult to get started? Maybe. It depends upon whether or
not a year-round campground space near adequate medical capacity could
be located.

Could it be staffed? That's probably the easiest part. How many
professors and other teachers have lost their jobs recently due to
closings and cutbacks?

Could it be run by one person? \textbf{No!}. A board would definitely
need to be recruited.

That I am totally ripping off a plan from the later part of the
Honorverse series by David Weber should show people have thought of this
before. I would be basing it on a structure mentioned in one of the much
later books found in the Verge during the Solarian League campaign. A
competitive league was used in the story as a means to organize and
maintain communications as well as hope. A camp in a situation like this
would simply be a health/wellness camp that would \emph{not} have a
formal credit-granting academic program.

It \emph{could} be doable. It isn't something I have the capacity to get
the ball rolling on by myself, though. Securing land to the tune of at
least 200-300 acres, essential utilities and sanitation, necessary
buildings, and other required things are not simple things to bootstrap.
