How best can I put this? This is not a good time to be an American. Down
the street from me I have a neighbor with a flagpole in their front
yard. They're proudly flying a black flag that says ``ULTRA MAGA''. The
number of ``Stars and Bars'' flags flying in the local area have been
increasing rather precipitously too. By looking at the area now you'd
never think that this was one of the hotbeds of abolitionism at the time
of the Civil War and one of the northern terminii of the Underground
Railroad.

We have two very old men running for the office of President of the
United States. One of them is effectively a \emph{cult leader}. His
followers locally are kinda sorta fanatical. I can't prove it but I do
think some of the county central committee for the GOP were in the
vicinity of the events of J6. After all, the Facebook page of the county
party was used for coordinating transportation to the coup attempt in
part. These are people locally that are willing to use force.

That's probably why I've stopped with any letters to the editor locally.
I would like to not see my house burned to the ground with me in it.
We've had a wave of mysterious arson cases lately and I don't want to be
the next victim. This technically means I have been successfully
intimidated, though.

Yes, I am one of those people looking at options to flee if Donald John
Trump wins the presidency again. I have rare and odd medical issues to
worry about. I stand a fairly decent risk of being deemed expendable and
not worth treating if the plans outlined in the Project 2025 playbook
get adopted. No amount of increased personal responsibility will help me
avoid what is effectively a \emph{genetic} condition. Work requirements
don't accomplish much when you wind up needing a whole lotta
multi-systemic cancer screening a wee bit earlier than the general
population does. Since the diagnosis in March 2023 it winds up being the
case that any visit to the doctor's office now has the potential to turn
into a general article if the presenting issue is sufficiently weird.
The healthcare section spends a bizarre amount of time discussing the
Assimilative Crimes Act and how it is to be used to ensure that criminal
law bans on abortion in certains \emph{shall apply in federal facilities
in those states} by choice of the administration-in-waiting. Fleeing an
incoming Trump administration would be to ensure I have access to the
care I need.

Again, I don't like this mess. We have a bunch of heretical fanatical
maniacs that want to run the country in the fashion of some warped and
twisted facsimile of ``the way things were'' that bears no connection to
reality. I get that ``Weimar feeling'' day by day lately as we see Trump
spew nonsense and increasingly look like he's not well.

Going to Canada is \textbf{not an option} due to problems with the
health system there. Australia or the UK would be the options that would
at least keep me connected to the combined research group for The
Condition. Melbourne \& Sydney have researchers there that have
previously worked with the combined group. There is a researcher in the
UK in Southampton who has also worked with the group. The main body of
researchers is based at Cleveland Clinic, of all places. I'm located
just a short drive away now from the leading researchers on the planet
but we're all in an area that could get very dangerous as the year
continues.

What a mess\ldots{}
