Why on earth am I even trying to get started with
\href{https://patreon.com/erielookingproductions?utm_medium=unknown&utm_source=join_link&utm_campaign=creatorshare_creator&utm_content=copyLink}{Patreon}?
Well, as the title says, things are not as stable as they might seem.
While I may enjoy teaching I recognize that my position is
\emph{contingent} and right now there are many politicians that want to
gut funding for technical and further education. On Wednesday I get to
see the farce of
\href{https://web.archive.org/web/20240512220301/https://www.wtrf.com/news/education/local-college-offering-scholarships-to-students-involved-in-eastern-gateway-community-college-upheaval/}{Eastern
Gateway Community College} here in Ohio have one of its final board
meetings as it begins the final steps towards dissolution in the face of
a budget crisis. Lakeland Community College is nearing
\href{https://web.archive.org/web/20240512130552/https://ohioauditor.gov/fiscal/local.html}{``fiscal
watch''} status with the Auditor of State so it is close but not yet
over the edge in terms of budget problems. Out of the 34 public
institutions of higher learning in Ohio only The Ohio State University
and University of Cincinnati are in okay shape financially at the
moment.

Yes, I am teaching across the state line in Pennsylvania. I would be a
fool to not recognize that even
\href{https://web.archive.org/web/20240512122317/https://www.wesa.fm/education/2024-05-12/penn-state-commonwealth-campus-buyouts-budget-cuts}{The
Pennsylvania State University is dipping into a voluntary separation
program with staff at its outlying branch campuses}. We're in good shape
at the moment where I am teaching but having a contingency plan would be
good business sense at this point.

I don't know what is coming. The uncertainties posed by the impending
presidential election are not helping. The angry old man from Mar-A-Lago
is going around
\href{https://web.archive.org/web/20240513140912/https://www.independent.co.uk/news/world/americas/us-politics/trump-hannibal-lecter-new-jersey-rally-b2544094.html}{praising
Hannibal Lecter at rallies now for no fathomable reason}.

The only jobs being posted locally are at Ashtabula County Medical
Center and they're to fill positions that the hospital has been trying
to fill for a couple years now. Even retail and food service employers
aren't even looking locally. That's the kind of bad condition the
economy locally is in right now. Of course, it has been in that
condition for some time. Why else would I commute to Erie to work at
all?

I'm not sure I'm going to like the clarity that the election in November
might bring\ldots{}
