The \texttt{README.md} for this site says on Launchpad something fairly
curious. The new sentence added states:

\begin{quote}
\emph{We haven't gone }nomadic* yet but that is always possible.*
\end{quote}

Essentially I've been having to conceptualize from time to time what it
would look like to maintain a blog \emph{off-line} in a git repo that
was distributed through unusual means. For example, what would a blog
look like if a base \href{https://www.git-scm.com/docs/git-bundle}{git
bundle} were distributed and then had updates sent via
\href{https://git-scm.com/docs/git-format-patch}{git-format-patch} that
were applied using \href{https://git-scm.com/docs/git-am}{git-am}? You'd
essentially have a living document set that would be a self-contained
off-line website potentially if you used a static site generator like
\href{https://jekyllrb.com}{Jekyll}. It would depend if you wanted to
ship your entire source or just the final build product, I suppose.

You couldn't use \href{https://git-lfs.com}{Git Large File Storage} with
such a thing since it would introduce an external dependency on a server
and \href{https://jekyllrb.com}{Jekyll} doesn't play nice with it
anyhow. RSS wouldn't exactly work well with it either. Shipping binary
bits would need to be limited.

Conceivably this could also be done with
\href{https://rust-lang.github.io/mdBook/}{mdbook} and might make more
sense that way. Shifting from a blog to ``Captain's Log\ldots{}'' would
fit such a note in the bottle style of distribution.

Why even think of something like this? I am based in a rural area that
the MAGA people would easily forget about and leave behind in their
plans for retribution and dominance. Alternative and oddball
communications methods are likely to be essentially in 2025 if that
alleged criminal returns to being President of the United States.
