Well, now things are going to get messy. Elected leaders across the
country are tiring of the pro-Palestinian protests. It seems Ohio
Attorney General Dave Yost is getting ready for not just mass arrests
but also many, many prosecutions.

WJW Cleveland
\href{https://web.archive.org/web/20240508235750/https://fox8.com/news/ohio-ag-anti-kkk-charges-for-student-protestors-in-masks/}{reports}
that the AG has written to the presidents of the state's public
universities and colleges. The AG told them to warn student protesters
that they may be liable to prosecution under the anti-disguise law. The
law in question dates back to 1953.

\href{https://codes.ohio.gov/ohio-revised-code/section-3761.12}{Section
3761.12 of the Ohio Revised Code} simply states: ``No person shall unite
with two or more others to commit a misdemeanor while wearing white
caps, masks, or other disguise.''

That section needs to be read in concert with
\href{https://codes.ohio.gov/ohio-revised-code/section-3761.99}{section
3761.99 of the Ohio Revised Code} which states: ``Whoever violates
section 3761.12 of the Revised Code is guilty of a felony of the fourth
degree.''

What misdemeanor could be utilized? Probably trespass as defined in
\href{https://codes.ohio.gov/ohio-revised-code/section-2911.21}{section
2911.21 of the Ohio Revised Code}.

Why reach for tools like this? Well, the legislature in its infinite
wisdom decided to restrict the operational authority of the public
colleges and universities. For as much as Republican legislators here in
Ohio want the protests to stop, they also happen to be the same people
that
\href{https://codes.ohio.gov/ohio-revised-code/section-3345.0213}{enacted
provisions tightly restricting acaademic administrators at the public
institutions from shutting down any outdoor protests at all}. We've had
a Republican supermajority in state legislature for over a decade so it
isn't like a Democrat snuck that provision in somewhere to plan two
years in advance for these protests. They did themselves in on this one.

Mind you, this is the same state where four protesters were shot dead by
Ohio Army National Guard troops on the main campus of Kent State
University on May 4, 1970. Could it happen again? While every graduate
of Kent State University since that day in 1970 hopes it doesn't we're
also not blind to the realities around us. AG Yost is preparing to roll
the hard six and is playing for all the marbles. He is an ambitious
politician look at a run for governor in two years. Anything is
possible.

al Jazeere is updating the protests map found at
\url{https://www.aljazeera.com/news/2024/4/29/mapping-pro-palestine-campus-protests-around-the-world}.
It is missing some like the protest at Case Western Reserve University.
The latest CNN attempt to chart things can be found at
\url{https://www.cnn.com/2024/05/08/us/pro-palestinian-protests-arrests-colleges-dg/index.html}.
