Well, the United States Supreme Court dropped several opinions today.
This was the tail-end of a controversial group of opinions. Most of
these outcomes have been pretty bad.

As much as I might say something about the opinions I think I won't. The
simplest thing to say is that it is getting weird. I do think some lines
were crossed that we may not be able to easily handle.

If I were a regular person then this wouldn't be a big deal.
Unfortunately there are some unique problems that I face that put me in
some vulnerable spots with the way circumstances are coming together.
Right now I have access to the medical care that I need. That sort of
care would easily become imperiled if the angry man from Florida won
control of the federal government. Why? Well, one of the quarterbacks in
the federal government that
\href{https://ncats.nih.gov/research/research-activities?related_office\%5B\%5D=2\#research-activities-at-NCATS}{helps
advance research} to provide better care for folks in my situation would
be abolished in the Project 2025 plans. Research funding
\href{https://ncats.nih.gov/research/research-activities/rdcrn}{would be
gone}. There is \href{https://www.ptenresearch.org}{the research
foundation} but their resources hardly match the US Government's.

Running would be nice but there aren't exactly many places to run to
based upon where the specific patient organizations are. There is a
\href{https://ptenuki.org/}{UK/Ireland group} as well as an
\href{https://www.ptenitalia.org/}{Italian group},
\href{https://www.shg-cobald.de/}{a German group},
\href{https://www.syndromedecowden.com/}{a French group}, a
\href{https://ptenbelgienederland.nl/}{Belgian group}, and a
\href{https://ptenfoundation.org/}{US group}. There is a
\href{https://www.ptenworld.com/pten-world}{global support website} but
that has its limits. When I last looked at the registry the places with
the largest concentrations of known patients shown in the registry were
the US, Canada, Italy, Australia, the UK, and Ireland. The world experts
are at Cleveland Clinic.

This is an overall bad scenario. I'll have to think about it a bit.
We'll end up seeing just how numb Americans are, I think.
