Apparently Republican party adherents in Iowa
\href{https://web.archive.org/web/20240116055624/https://www.france24.com/en/americas/20240116-donald-trump-projected-to-win-iowa-republicans-caucuses}{favor
having an accused criminal as the party's standard bearer in the
campaign for President of the United States}. apparently
\href{https://web.archive.org/web/20240116031827/https://news.sky.com/story/donald-trump-projected-to-win-iowa-caucuses-13049306}{Vivek
Ramaswamy had dropped out of the running}. President Biden
\href{https://web.archive.org/web/20240116060245/https://www.dw.com/en/iowa-caucus-donald-trump-wins-first-republican-contest/live-67991224}{is
already calling the accused criminal \emph{the clear frontrunner in the
race}}. The next match-up is in New Hampshire
\href{https://web.archive.org/web/20240116060554/https://www3.nhk.or.jp/nhkworld/en/news/20240116_22/}{on
January 23rd}.

Yes, I \emph{was} holding out hope for an outbreak of sanity. My country
is giving up on democracy, its history, and more. We're going down the
``man on a white horse'' route of wanting the aveging hero to come save
the day. The big problem is that people think this accused criminal and
failed coup plotter is some sort of hero. He's a villain!

Running away is not really an option at this immediate moment. After
all, where could I go? The list of
\href{https://rarediseases.org/rare-disease-centers-of-excellence/}{possible
supporting institutions} is not really that big and even that list is
full of non-starters. It is also US-only. There is a listing of
\href{https://www.orpha.net/consor/cgi-bin/SupportGroup_Search_Simple.php?lng=EN&LnkId=21218&Typ=Pat&fdp=y&from=rightMenu}{supporting
organizations world-wide according to orphanet} but it has very, very
limited options in English-speaking areas that seem restricted to
Australia, Canada, USA, and the United Kingdom. Following the footsteps
of Matoaka to the UK would be utterly hilarious but an
\href{https://www.royalmarsden.nhs.uk/our-consultants-units-and-wards/clinical-units/cancer-genetics-unit}{``expert
centre''} is located there according to orphanet.

I know this caucus outcome was expected. That doesn't mean it isn't
annoying.
