I'm not sure what to do with much of this anymore.

From
\href{https://www.avclub.com/george-carlin-ai-stunt-cant-compare-to-the-real-thing-1851161376}{\emph{The
AV Club}} we have a piece entitled ``Today feels like a good day to
ignore dumb AI stunts and watch the real George Carlin''. No, it is not
a happy read. These are frontiers that should \textbf{not} be explored

A pertinent quote:

\begin{quote}
\emph{Earlier this week, ``news'' broke that quickly caused a lot of
people to disregard Paul Anka's classic advice on monsters (and whether
you should give them the precious, life-giving attention that they
crave): The announcement that some folks (including, bizarrely, former
Mad TV star Will Sasso) had fed a bunch of routines from late stand-up
comedy legend George Carlin into an AI and caused it to shit out an hour
of ``stand-up'' presented in a digital facsimile of Carlin's voice.}
\end{quote}

No, this is not good. WHY WOULD YOU DO THIS? The man has a corpus of
work that is defined. Trying to create continuing adventures that
appropriate his voice and likeness is sacrilege.

There was coverage in
\href{https://variety.com/2024/digital/news/george-carlin-ai-generated-comedy-special-1235868315/}{\emph{Variety}}
as well that I missed. This detail was a key point that bothers me:

\begin{quote}
\emph{The hour-long special, which dropped on Tuesday, comes from
Dudesy, a comedy AI that hosts a podcast and YouTube show with ``Mad
TV'' alum Will Sasso and podcaster Chad Kultgen.}
\end{quote}

Dudesy? There is an AI named Dudesy? It isn't as if the coverage in
\href{https://www.polygon.com/24034625/george-carlin-i-wish-i-was-dead-ai-comedy-special-kelly-carlin-dudesy}{\emph{Polygon}}
gives any inkling as to what model the thing is running on. I found
something on HuggingFace
\href{https://huggingface.co/njwrigh92/t-5-comedy}{that claims to be a
stand-up comedian's \emph{assistant}} but not a standalone model to run
rampant. The folks at
\href{https://www.theregister.com/2024/01/12/george_carlin_comedian_cloned/}{\emph{The
Register}} did find that there is statutory law in Tennessee about using
AI for things like this but that may not be the most helpful thing at
the moment.

If this is any indication of what may be coming, nobody is going to know
what is real or not as we head into the 2024 presidential campaign.
That's going to be dangerous. \textbf{Life is horrifying when it starts
to resemble a John Ringo novel.}
