The headline in \emph{Deadline} is horrible. What does it say?

\href{https://web.archive.org/web/20240613001814/https://deadline.com/2024/06/trump-guillotine-kathy-griffin-1235971973/}{Trump's
``Haul Out The Guillotine!'' Fundraising Email --- Invoking Kathy
Griffin --- Draws Biden Counter Pitch}

The coverage in
\href{https://web.archive.org/web/20240613052045/https://newrepublic.com/post/182620/trump-message-followers-dark-turn-guillotine}{\emph{The
New Republic}} is not much better. The
\href{https://archive.org/details/tv?q=trump+guillotine&and\%5B\%5D=publicdate\%3A\%5B2009-06-04+TO+2024-06-13\%5D&red=1&sort=-addeddate}{TV
News Search from the Internet Archive} didn't find any mentions of it in
captions logged to the system there. That would explain the Tommy
Christopher article over at \emph{Mediaite} entitled
\href{https://web.archive.org/web/20240612211506/https://www.mediaite.com/news/nobodys-made-a-big-deal-cnns-jim-acosta-stunned-trumps-beheading-themed-email-hasnt-gotten-more-attention/}{`Nobody's
Made A Big Deal!' CNN's Jim Acosta Stunned Trump's Beheading-Themed
Email Hasn't Gotten More Attention}. Axios talks about the matter in a
piece entitled
\href{https://web.archive.org/web/20240613032346/https://www.axios.com/2024/06/12/trump-guillotine-fundraising-email-democrats}{``Haul
out the Guillotine,'' Trump says in fundraising email}.

Between that Axios report and
\href{https://web.archive.org/web/20240607223852/https://www.axios.com/2024/06/06/trump-hannity-biden-prosecution-fox-news}{one
in Axios where it is reported that Trump stated he will pursue his
enemies if elected}, there are things to be considered here. First and
foremost, how many of his followers are accepting this as a call to
commit violence in support of him? After all, one of the January 6th
rioters who is in prison at the moment
\href{https://web.archive.org/web/20240612203847/https://www.wired.com/story/january-6-rioter-leading-armed-national-militia-from-prison/}{is
reportedly establishing a new militia across the country at the moment
on a cellular structure} per \emph{WIRED}. Even if other groups were
broken thanks to the prosecutions, the sheer scale of the situation and
how long the prosecutions has taken has allowed the conspiracy to
regroup and reform.

Trump is being sentenced on July 11th. Contingency plans should be
established, I suppose.
