In today's posts from \emph{Ohio Capital Journal} they had a beautiful
op-ed from Doug Oplinger who previously worked for \emph{Akron Beacon
Journal} for many years. In his article
\href{https://web.archive.org/web/20240424184708/https://ohiocapitaljournal.com/2024/04/24/for-whom-the-bellwether-tolls-is-ohio-an-omen/}{he
talks about Ohio being an omen}. What is it an omen of? Well, we often
have the marketing slogan in this state that Ohio is the heart of it
all. To pull a particular quote from the article, I'll note that
Oplinger wrote in pertinent part:

\begin{quote}
\emph{But first, let's back up. What's a bellwether? It's the predictor.
From 1896 to 2016, the majority of Ohioans voted for the presidential
winner on all but two occasions. Thus, the old saying was, ``As Ohio
goes, so goes the nation.''}
\end{quote}

The streak broke in 2020 when the state went for Trump instead of Biden.
The op-ed continues to talk about the anxiety and despair happening here
in the Buckeye State. I've mentioned previously that \emph{The
Washington Post} has a syndicated article out there
\href{https://web.archive.org/web/20240105093608/https://www.unionleader.com/news/health/how-red-state-politics-are-shaving-years-off-american-lives/article_a15969c1-6959-526b-91d2-9d1c966c15fd.html}{talking
about how much of a disaster Ashtabula County is in terms of its economy
and the health of its residents}. The whole state is in bad shape but
Ashtabula County more resembled a Third World area compared to its
neighboring communities which is why it caught the attention of the
folks at the \emph{Post}.

Ohio is a huge part of the engine that fuels the insurrectionists and
continuing heartbeat of the MAGA movement. Ohioans make up far more of
the J6 insurrectionists than should be expected. We have militia groups
training here and plotting actions. We have Christian nationalists
building power bases here. Far too many Ohioans are okay with tyranny
and retribution as they think they are being somehow oppressed and need
to fight back. They feel that no help is coming and that they have
nothing to lose.

You know it is a bad situation when I am too afraid to write a letter to
the editor locally. When I looked at this week's edition of \emph{The}
(Jefferson, Ohio) \emph{Gazette} there were only letters from rabid MAGA
partisans. Frankly I'm worried about having my house burned down if
people get upset at something I wrote. The number of MAGA people and
MAGA-adjacent people acting out has been slowly increasing.

What a mess. There's no ripcord to pull, really. We don't need another
cult on the order of the Millerites facing another Great Disappointment
this November. That way can only lead to instability.
