Well, the attempt to shift to using \texttt{mdbook} for this site went
poorly. I've ported over what I write in mdbook to the site as four
posts. For now I am back to Jekyll, it seems.

It is increasingly looking dangerous to blog. What a strange world we
live in. I did maintain a neat list of podcasts in the mdbook site
reflecting what I was listening to. It stated:

\begin{itemize}
\item
  \href{https://mwl.io/}{60 Seconds of WIP}
  \href{https://mwl.io/feed/60sow-mp3}{(Feed)}
\item
  \href{https://69admins.com/}{69 Admins}
  \href{https://feeds.acast.com/public/shows/6410a80dec813e00110faed2}{(Feed)}
\item
  \href{https://www.gerryanderson.com/}{Anderson Audio Adventures}
  \href{https://feeds.captivate.fm/andersonaudioadventures/}{(Feed)}
\item
  \href{https://www.theincomparable.com/tpk/candlekeep/}{Candlekeep
  Mysteries (from Total Party Kill)}
  \href{http://feeds.theincomparable.com/tpk/candlekeep}{(Feed)}
\item
  \href{https://www.abc.net.au/listen/programs/downloadthisshow/}{Download
  This Show}
  \href{https://www.abc.net.au/feeds/12801214/podcast.xml}{(Feed)}
\item
  \href{http://freetoagoodhome.libsyn.com/}{Free to A Good Home}
  \href{https://feeds.acast.com/public/shows/60e5013bce8a4200126b891c}{(Feed)}
\item
  \href{https://www.abc.net.au/listen/programs/if-youre-listening/}{If
  You're Listening}
  \href{https://www.abc.net.au/feeds/9593214/podcast.xml}{(Feed)}
\item
  \href{https://www.theincomparable.com/robot/}{Robot or Not?}
  \href{https://feeds.theincomparable.com/robot}{(Feed)}
\item
  \href{https://www.savethed8pod.com/}{Save The D8}
  \href{https://anchor.fm/s/796a788/podcast/rss}{(Feed)}
\item
  \href{https://linktr.ee/sysw}{System Switch}
  \href{https://anchor.fm/s/83b36ba8/podcast/rss}{(Feed)}
\item
  \href{http://talesfromtrantor.com/}{Tales from Trantor - An Australian
  TTRPG Podcast} \href{https://talesfromtrantor.libsyn.com/rss}{(Feed)}
\item
  \href{http://esoteric-rp.blogspot.com/}{The Esoteric Order of
  Roleplayers}
  \href{https://feed.podbean.com/esotericrp/feed.xml}{(Feed)}
\item
  \href{https://gerry-anderson-randomiser.captivate.fm/}{The Gerry
  Anderson Randomiser}
  \href{https://feeds.captivate.fm/gerry-anderson-randomiser/}{(Feed)}
\item
  \href{https://www.theincomparable.com/gameshow/}{The Incomparable Game
  Show} \href{https://feeds.theincomparable.com/gameshow}{(Feed)}
\item
  \href{https://www.theincomparable.com/radio/}{The Incomparable Radio
  Theater} \href{https://feeds.theincomparable.com/radio}{(Feed)}
\item
  \href{https://theloneadventurer.podbean.com/}{The Lone Adventurer}
  \href{https://feed.podbean.com/theloneadventurer/feed.xml}{(Feed)}
\item
  \href{https://www.theincomparable.com/tpk/}{Total Party Kill}
  \href{https://feeds.theincomparable.com/tpk}{(Feed)}
\item
  \href{https://www.relay.fm/ungeniused}{Ungeniused}
  \href{https://www.relay.fm/ungeniused/feed}{(Feed)}
\item
  \href{https://www.wired.com/}{WIRED Politics Lab}
  \href{https://publicfeeds.net/f/5802/have-a-nice-future}{(Feed)}
\end{itemize}

Regular blogging to resume soon?
