Well, maintaining a blog like this is probably something most probably done in anger in \LaTeX.  What can I say?  I went ahead and even created a GitHub Action to rebuild the web page using LaTeXML whenever I add something new and push the updates to the repo.  That's probably when you end up taking the "anger" and are then taking it to absurd directions.

Speaking of absurdity, we have this mess:

\begin{quote}
    Via \href{https://universeodon.com/@memorandum}{@memeorandum@universeodon.com}: \url{https://universeodon.com/@memeorandum/113658575822842517} \#retoot

    Post by memeorandum. "Trump and His Picks Threaten More Lawsuits Over Critical Coverage (David Enrich/New York Times) nytimes.com/2024/12/15/busines… memeorandum.com/241215/p24\#a24…" Posted on Dec 15, 2024 at 14:50

\end{quote}

I'm not sure that's going to slow down.  If anything it'll make podcasting more dangerous.  I \emph{could} go down the road of releasing podcasts encoded in Opus that are crushed very, very hard in terms of bitrate so that they could be snuck around as very small files.  Who would listen to that, though?

In other news\ldots 

\begin{itemize}
\item Church went very well this morning.  Today's service can be found at \url{https://www.youtube.com/live/uFv6W7jnUg4} and features a baptism.  We did very well filming the baptism and got through all the stage management quite well.  I wish we had baptisms more often.
\item Yes, I am dreading the coming Trump administration.
\item I got some treadmill time in and it felt good.
\item I'm basically off-duty with any teaching responsibilities until early February.  That will cut down the income here at home.
\item I'll get back into the swing of doing things soon enough, I suppose, in \LaTeX. 
\end{itemize}

