Well, after I submit my grades I am done teaching for hte year. That'll
be five regular semesters of teaching on the books plus two summer
semesters. After all the \emph{sturm und drang} of undergraduate and
graduate school who would have thought that \emph{THIS} was where I
needed to be in life?

The only major event that I have coming up is the Christmas Eve service
at Geneva Church of Christ. I may actually be on stage as part of the
praise team singing that night. Usualy I am in the back handling tech
matters so it would be a nice switch.

I will be needing to working on some curriculum things between now and
the start of the spring semester. Thankfully the spring semester doesn't
start until February. That's an artifact of all the COVID waves and us
trying to avoid starting classes in the middle of them. That gives me
time to get ready to teach the new classes in the spring that I haven't
taught before.

I do intend to visit \url{https://startplaying.games} to see about
finding a pickup game or two. I need to take a break and relax. More
than likely I would be looking for something in the realm of
\href{https://startplaying.games/search?gameSystems=traveller}{Traveller}
or
\href{https://startplaying.games/search?gameSystems=cyberpunk-2020&gameSystems=cyberpunk-red}{Cyberpunk}.
I would not be averse to something from the realm of the
\href{https://startplaying.games/search?gameSystems=tiny-cthulhu&gameSystems=tiny-dungeon&gameSystems=tiny-supers}{Tiny
D6 system} even though it is a bit more obscure.

The planning to flee continues. The question of
\href{https://simple.wikipedia.org/w/index.php?title=Passport&oldid=9380185}{passports}
is still being worked on even though the matter of
\href{https://simple.wikipedia.org/w/index.php?title=Convention_Relating_to_the_Status_of_Refugees&oldid=9477226}{seeking
asylum} grows simpler with nominees like
\href{https://simple.wikipedia.org/w/index.php?title=Robert_F._Kennedy_Jr.&oldid=9916838}{the
Secretary-designate of Health and Human Services} who are dangerous to
people with various medical conditions.

This is not how I wanted this year to end. We'll see how things go, I
suppose.
