What is it like living in a town where people are quite often part of
the Trump cult?

Well, it isn't pretty. As Trump continues to meltdown we have people
sticking with him. This is \emph{cult} behavior after all. The great
leader is never wrong.

I'm not sure how exactly people extricate themselves from this. What
happens when they potentially face their Great Disappointment later this
year? Frankly I am expecting violence.

I have some
\href{https://humanrights.gov.au/our-work/asylum-seekers-and-refugees/asylum-seekers-and-refugees-guide}{reading
I need to do} with all the coercive chatter from the MAGA types lately.
The risk of Trump winning remains still too high for my comfort. Things
like the
\href{https://www.presidency.ucsb.edu/documents/2024-republican-party-platform}{GOP
2024 platform} don't really have places in them for
\href{https://my.clevelandclinic.org/health/diseases/24548-pten-hamartoma-tumor-syndrome}{those
that are outside the norm}. After all, talk of ``benefit flexibility''
in that platform means cost containment and trying to eliminate usage of
health care resources to the extent possible.

I've been living in a town where people don't go to the doctor. People
don't spend money on taking care of themselves. People actively choose
to smoke cigarettes to the point of imitating chimneys. The effects of
this ``flexibility''
\href{https://www.washingtonpost.com/health/interactive/2023/republican-politics-south-midwest-life-expectancy/}{are
well documented}.

Things are on fire, metaphorically speaking, and it is not okay\ldots{}
