\textbf{Thursday, November 14, 2024}
The appointments dribbling out from the apparent president-elect, Donald
John Trump, have been truly frightening. I'm not quite sure where things
are heading. It doesn't look like they're heading anywhere good.

\textbf{Friday, November 15, 2024}
The nomination of RFK Jr.~to be Secretary of Health and Human Services
is quite dangerous. Will this impact the ability of providers to treat
The Unmentionable Condition? Oh, more than likely. I can't see this guy
allowing the Orphan Drug Act to properly operate let alone
\href{https://rarediseases.info.nih.gov/resources}{other resources in
HHS} of special interest to me.

We've progressed beyond the clown car to something more insidious. I'm
not even sure what to term it. This is just bad overall.

The passport should be arriving soon. This helps move plans forward.

Is it time to cross the Rubicon? It seems so if they let this craziness
proceed. I can't take bets on whether or not the badness will happen but
right now this isn't making much sense.

\textbf{Saturday, November 16, 2024
(Overnight)}
My passport arrived Friday. This is very much \textbf{a good thing}.
This allows evacuation planning to proceed.

The clown car continues to fill up as the new administration continues
to take form and shape. Frankly this is horrifying.

This weeks edition of \emph{The Gazette} showed up late as it was in the
mailbox Friday instead of Thursday. We're seeing the death of news play
out before us here in Ashtabula County. The problem is that for the most
part \emph{people don't care locally}. Having a dearth of active news
entities also corresponds to high voter turnout for Donald Trump and
that hypothesis is born out here in Ashtabula County.

I'm not sure what all is coming. That simply seem to be dark clouds on
the horizon. Optimism seems totally out of place at this time.

\textbf{Saturday, November 23, 2024}
In no particular order:

\begin{itemize}
\item
  It looks like I will \emph{not} be traveling for Thanksgiving
\item
  Podcasting continues
\item
  The degree of terror from Trump's nominees for cabinet and sub-cabinet
  continues to rise
\item
  I'm not liking where much of this is going lately
\end{itemize}

\textbf{Thursday, November 28, 2024
(Overnight)}

I think something broke when I added the new theming. When I build
locally everything is fine. The build by GitHub Actions breaks, though.
I \emph{could} just build locally but I don't want to do that if I can
help it.

Oh, by the way, today is Thanksgiving. It's supposed to be happy, I
guess\ldots{}
